### 2015-03-31 doc/proposal/paper.tex
Add proposal template

\documentclass[letterpaper,twocolumn,10pt]{article}

\usepackage{style, verbatim, url}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}
\usepackage{cleveref}
\usepackage{breakurl}

\makeatletter
\newcommand{\crefnames}[3]{
    \@for\next:=#1\do{
        \expandafter\crefname\expandafter{\next}{#2}{#3}
    }
}
\makeatother
\crefnames{part,chapter,section}{\S}{\S\S}

\begin{document}

\title{\Large \bf A Transparent Peer-to-Peer CDN}

\author{
    {\rm Anish Athalye}\\
    aathalye@mit.edu
    \and
    {\rm Ankush Gupta}\\
    ankush@mit.edu
    \and
    {\rm Katie Siegel}\\
    ksiegel@mit.edu
}

\maketitle

\thispagestyle{empty}

\begin{abstract}

\end{abstract}

\section{Introduction}

\section{Design}

\section{Goals}

{\footnotesize \bibliographystyle{ieeetr}
\bibliography{paper}}

\end{document}

### 2015-04-01 doc/proposal/paper.tex
Add proposal

@@
 
-\title{\Large \bf A Transparent Peer-to-Peer CDN}
+\title{\Large \bf Zauberfl\"{o}te: A Transparent Peer-to-Peer CDN}
 
@@
 
-\begin{abstract}
+\section{Introduction}
 
-\end{abstract}
-
-\section{Introduction}
+Currently, peer-to-peer content delivery networks exist, yet are usually
+closed-source. PeerCDN is one such example found in industry; it offloads site
+hosting to users of a site, significantly lowering strain on content delivery
+from a central source. In our project, we aim to create an open-sourced system
+that will allow developers to easily integrate a peer-to-peer CDN to expedite
+content delivery to clients even when operating under heavy load. We plan to
+base our design on the BitTorrent protocol~\cite{cohen:bittorrent}, where
+clients requesting content will attempt to receive chunks of data from other
+clients rather than a central server. We plan to begin with tracker software
+and then add client software for communicating with the tracker and sharing
+content with peers.
 
@@
 
+We plan to implement a peer-to-peer CDN using a hybrid HTTP/P2P setup. For the
+peer-to-peer part of the service, we will use a BitTorrent-like protocol to
+share data between clients. We will use intelligent client software that uses
+both HTTP and P2P to minimize latency and maximize throughput.
+
+We will have a centralized tracker, a server that keeps track of file metadata
+and facilitates matchmaking between peers. This server will not host the file
+contents themselves. The server will make use of cryptographic hash functions
+to guarantee the integrity of data and prevent malicious clients from
+distributing bad data.
+
+We will have a separate HTTP server to serve content and bootstrap peers when
+there are no other clients with a copy of the content.
+
+On the client side, we plan to use only HTML5 APIs to communicate with our CDN.
+This will make it simple to start using the CDN, and all clients with
+up-to-date browsers will just work with the service. The process will be
+entirely transparent to end users, because it will not require the use of
+browser extensions or other custom software that has to be manually installed.
+We plan to make use of WebRTC for peer-to-peer functionality~\cite{w3c:webrtc}.
+
 \section{Goals}
+
+Zauberfl\"{o}te provides basic framework of peer-to-peer content delivery on
+which other systems can be built. We plan to build in the initial
+infrastructure and then conduct tests to evaluate the performance of the
+system.
+
+To demonstrate the robustness of our peer-to-peer CDN system, we plan to
+measure the latency of several large data transfers and compare this
+performance to that of a simple centralized system. Our results will help
+identify scenarios in which such peer-to-peer CDN systems enhance the
+performance of an application.
+
+After measuring the performance of our system, we intend to work on decreasing
+the latency involved with obtaining large resources on the internet by allowing
+data transfer from peers, rather than a central server, when operating under
+heavy load. At the same time, we want to attempt to ensure that page loads are
+not any slower than they would be with the use of only a central server by
+heuristically evaluating the load times of data via peer-to-peer transfers as
+compared to downloading from the central server.
+
+Potential extensions include peer-to-peer video streaming and multiplayer
+gaming. We hope that the latency decrease in such applications would be
+significant, leading to a better overall user experience.
 

### 2015-05-01 src/fiddler/frontend.js
remove handholding ui code

@@ -9,11 +9,12 @@ socket.on("connect", function(){
 socket.on("peer-reply", function(data) {
   peers = data.peers;
   console.log(data.peers);
+  var item = $("[data-zauberflote=" + data.hash + "]")[0];
   if (data.peers.length ==  0) {  
-    var item = $("[data-zauberflote=" + data.hash + "]")[0];
     item.src = $(item).attr("data-original");
     socket.emit("add", data.hash);
   } else {
+    item.className = item.className + " waiting";
     start();
   }
 });
@@ -156,25 +157,6 @@ var o = signalingChannel.onmessage;
 // -------------------------------------------------
 
 $(document).ready(function() {
-  var adButton = $(document.getElementById("advertise-button"));
-  var askButton = $(document.getElementById("ask-button"));
-  var contentInput = $(document.getElementById("content-input"));
-  var contentOutput = $(document.getElementById("content-output"));
-  var hashInput = $(document.getElementById("hash-input"));
-
-  adButton.on("click", function() {
-    var content = contentInput.val();
-    var hash = Sha256.hash(content);
-    socket.emit("add",hash);
-    console.log(hash);
-  });
-
-  askButton.on("click", function() {
-    var hash = hashInput.val();
-    socket.emit("peer-request", hash);
-  });
-
-
   // auto p2p
   var p2pAssets = $(".zauberflote-item");
   for (var i = 0; i < p2pAssets.length; i++) {

### 2015-05-01 src/fiddler/frontend.js
Add XHR example to fetch binary data and load it

@@ -1,186 +1,30 @@
-// -------------------------------------------------
-// WEBSOCKETS
-// -------------------------------------------------
-var socket = io("http://localhost:5000");
-var peers = [];
-socket.on("connect", function(){
-  console.log("connected socket!");
-});
-socket.on("peer-reply", function(data) {
-  peers = data.peers;
-  console.log(data.peers);
-  if (data.peers.length ==  0) {  
-    var item = $("[data-zauberflote=" + data.hash + "]")[0];
-    item.src = $(item).attr("data-original");
-    socket.emit("add", data.hash);
-  } else {
-    start();
-  }
-});
-socket.on("webrtc-data", function(data){
-  signalingChannel.onmessage(data);
-});
-socket.on("disconnect", function(){
-  console.log("disconnected socket");
-});
 
-
-
-
-// ------------------------------------------------
-// WEBRTC
-// ------------------------------------------------
-
-
-// CONFIGS
-var IS_CHROME = !!window.webkitRTCPeerConnection,
-    RTCPeerConnection,
-    RTCIceCandidate,
-    RTCSessionDescription;
-if (IS_CHROME) {
-  RTCPeerConnection = webkitRTCPeerConnection;
-  RTCIceCandidate = window.RTCIceCandidate;
-  RTCSessionDescription = window.RTCSessionDescription;
-} else {
-  RTCPeerConnection = mozRTCPeerConnection;
-  RTCIceCandidate = mozRTCIceCandidate;
-  RTCSessionDescription = mozRTCSessionDescription;
-}
-var configuration = {
-  iceServers: [
-    {url: "stun:stun.l.google.com:19302"},
-    {url: "stun:stun1.l.google.com:19302"},
-    {url: "stun:stun2.l.google.com:19302"},
-    {url: "stun:stun3.l.google.com:19302"},
-    {url: "stun:stun4.l.google.com:19302"}
-  ]
-};
-var pc;
-var dataChannel;
-
-
-// SIGNALING CHANNEL
-function SignalingChannel(peerConnection) {
-  // Setup the signaling channel here
-  this.peerConnection = peerConnection;
-}
-SignalingChannel.prototype.send = function(peer, message) {
-  // Send messages using your favorite real-time network
-  console.log("Send:");
-  console.log(message);
-  // right now just get the first peer
-  var data = {"peer_id": peer, "data": message};
-  socket.emit("webrtc-data", JSON.stringify(data));
-};
[…]

### 2015-05-01 src/fiddler/frontend.js
datachannel sending assets

@@ -12,6 +12,7 @@ socket.on("peer-reply", function(data) {
   var item = $("[data-zauberflote=" + data.hash + "]")[0];
   if (data.peers.length ==  0) {  
     item.src = $(item).attr("data-original");
+    item.className = item.className + " received";
     socket.emit("add", data.hash);
   } else {
     item.className = item.className + " waiting";
@@ -111,6 +112,8 @@ function start() {
     ev.channel.onmessage = function(event) {
       console.log('got event in channel');
       console.log(event);
+      console.log(event.data);
+      console.log(JSON.parse(event.data));
     }
   };
 
@@ -120,8 +123,36 @@ function start() {
     console.log("I got data channel message: ", data);
   };
   dataChannel.onopen = function (event) {
-    dataChannel.send("Hello World!");
+    dataChannelSendAssets();
   };
+}
+
+function dataChannelSendAssets() {
+  dataChannel.send("hello world");
+  var receivedAssets = $(".zauberflote-item.received");
+  for (var i = 0; i < receivedAssets.length; i++) {
+    var image = receivedAssets[i];
+    // create an empty canvas element
+    var canvas = document.createElement("canvas"),
+        canvasContext = canvas.getContext("2d");
+    image.onload = function () {
+      //Set canvas size is same as the picture
+      canvas.width = image.width;
+      canvas.height = image.height;
+      // draw image into canvas element
+      canvasContext.drawImage(image, 0, 0, image.width, image.height);
+      // get canvas contents as a data URL (returns png format by default)
+      var dataURL = canvas.toDataURL();
+      console.log(dataURL);
+      var data = {"hash": $(image).attr("data-zauberflote"),
+        
+
+      dataChannel.send({
+        "hash": $(image).attr("data-zauberflote"),
+        "data": dataURL.toString()
+      });
+    };
+  }
 }
 
 function localOfferCreated(desc) {

### 2015-05-01 src/fiddler/frontend.js
p2p image transfer works

@@ -3,6 +3,7 @@
 // -------------------------------------------------
 var socket = io("http://localhost:5000");
 var peers = [];
+var assetData = {};
 socket.on("connect", function(){
   console.log("connected socket!");
 });
@@ -11,9 +12,7 @@ socket.on("peer-reply", function(data) {
   console.log(data.peers);
   var item = $("[data-zauberflote=" + data.hash + "]")[0];
   if (data.peers.length ==  0) {  
-    item.src = $(item).attr("data-original");
-    item.className = item.className + " received";
-    socket.emit("add", data.hash);
+    insertImage(item, data.hash);
   } else {
     item.className = item.className + " waiting";
     start();
@@ -26,6 +25,48 @@ socket.on("disconnect", function(){
   console.log("disconnected socket");
 });
 
+
+
+// -------------------------------------------------
+// FRONTEND DOC ELEMENTS
+// -------------------------------------------------
+
+$(document).ready(function() {
+  // auto p2p
+  var p2pAssets = $(".zauberflote-item");
+  for (var i = 0; i < p2pAssets.length; i++) {
+    var hash = $(p2pAssets[i]).attr("data-zauberflote");
+    console.log("emitting " + hash);
+    socket.emit("peer-request",hash);
+  }
+});
+
+function insertImage(item, hash) {
+  var src = $(item).attr("data-original");
+  var xhr = new XMLHttpRequest();
+  // note: CORS must be enabled
+  xhr.open("GET", src, true);
+  xhr.responseType = "blob";
+  xhr.onload = function(d) {
+    if (this.status == 200) {
+      var blob = this.response;
+      console.log(blob);
+      item.onload = function(e) {
+        window.URL.revokeObjectURL(item.src); // cleanup
+      };
+      item.src = window.URL.createObjectURL(blob);
+      var reader = new window.FileReader();
+      reader.readAsDataURL(blob); 
+      reader.onloadend = function() {
+        base64data = reader.result;                
+        console.log(base64data );
+        assetData[hash] = base64data;
+      }
+      socket.emit("add", hash);
+    }
+  };
+  xhr.send();
+}
 
 
 
@@ -112,8 +153,15 @@ function start() {
     ev.channel.onmessage = function(event) {
       console.log('got event in channel');
       console.log(event);
-      console.log(event.data);
       console.log(JSON.parse(event.data));
+      var assets = JSON.parse(event.data);
[…]

### 2015-05-01 src/fiddler/frontend.js
peer advertises once it gets it

@@ -159,7 +159,7 @@ function start() {
         if (assets.hasOwnProperty(hash)) {
           var item = $("[data-zauberflote=" + hash + "]")[0];
           item.src = assets[hash];
-          // item.src = window.URL.createObjectURL(atob(assets[hash]));
+          socket.emit("add",hash);
         }
       }
     }

### 2015-05-02 src/fiddler/main.go
Fix null pointer deref

@@ -3,6 +3,7 @@ package main
 import (
 	"log"
 	"net/http"
+	"strconv"
 	"sync"
 	. "types"
 
@@ -13,13 +14,18 @@ import (
 	"math/big"
 )
 
+type PeerRequest struct {
+	Seq  int    `json:"seq"`
+	Hash string `json:"hash"`
+}
+
 type PeerReply struct {
 	Hash  string   `json:"hash"`
 	Peers []PeerId `json:"peers"`
 }
 
 type WebRTCRequest struct {
-	Peer PeerId `json:"peer_id"`
+	Peer PeerId `json:"peer"`
 	Data string `json:"data"`
 }
 
@@ -48,16 +54,27 @@ func main() {
 				log.Println("ERROR AAAH")
 			}
 			webRTCdat := &WebRTCRequest{Data: request.Data, Peer: id}
-			peerSocket := tracker.GetSocket(request.Peer)
+			peerSocket, ok := tracker.GetSocket(request.Peer)
+			if !ok {
+				log.Println("invalid target", request.Peer)
+				return
+			}
 			log.Println("sending to peer for webrtc: ", webRTCdat)
 			(*peerSocket).Emit("webrtc-data", webRTCdat)
 		})
 
-		so.On("peer-request", func(hash string) {
-			log.Println("peer-request:", hash)
-			peers := tracker.Peers(hash)
-			reply := PeerReply{hash, peers}
-			so.Emit("peer-reply", reply)
+		so.On("peer-request", func(req string) {
+			log.Println("peer-request:", req)
+			var request PeerRequest
+			err := json.Unmarshal([]byte(req), &request)
+			if err != nil {
+				log.Println("error unmarshaling peer request")
+				return
+			}
+			peers := tracker.Peers(request.Hash)
+			reply := PeerReply{request.Hash, peers}
+			channel := "peer-reply-" + strconv.Itoa(request.Seq)
+			so.Emit(channel, reply)
 		})
 
 		so.On("disconnection", func() {
@@ -93,7 +110,7 @@ type Tracker interface {
 
 	Disconnect(id PeerId)
 
-	GetSocket(id PeerId) *socketio.Socket
+	GetSocket(id PeerId) (*socketio.Socket, bool)
 
 	Add(id PeerId, hash string)
 
@@ -135,8 +152,9 @@ func (tr *tracker) Disconnect(id PeerId) {
 	}
 }
 
[…]

### 2015-05-02 src/fiddler/peerdl.js
Implement peer download components
The patch adds the following components:
* Tracker
* SignalingChannel
* ConnectionManager

The patch includes some test code.

@@ -1,0 +1,238 @@
+'use strict';
+
+/**
+ * Utilities
+ */
+
+var DEBUG = false;
+
+function logError(error) {
+  if (DEBUG) {
+    console.log('error: ' + error);
+  }
+}
+
+/**
+ * Socket
+ */
+
+var skt = io("http://localhost:5000");
+
+/**
+ * Tracker Interface
+ */
+
+function Tracker(socket) {
+  this.socket = socket;
+  this.counter = 0;
+}
+
+Tracker.prototype.getPeersForHash = function(hash, callback) {
+  var seq = ++this.counter;
+  var req = {seq: seq, hash: hash};
+  this.socket.emit('peer-request', JSON.stringify(req));
+  this.socket.once('peer-reply-' + seq, function(data) {
+    if (data.hash === hash) {
+      callback(data.peers);
+    }
+  });
+};
+
+Tracker.prototype.addHash = function(hash) {
+  this.socket.emit('add', hash);
+};
+
+/**
+ * Signaling Channel
+ */
+
+function SignalingChannel(socket) {
+  this.socket = socket;
+  this.onmessage = null; // function taking (peer, data)
+  var that = this;
+  // set up handlers on socket
+  this.socket.on('webrtc-data', function(data) {
+    if (that.onmessage !== null) {
+      that.onmessage(data.peer, data.data);
+    }
+  });
+}
+
+SignalingChannel.prototype.send = function(peer, data) {
+  var req = {peer: peer, data: data};
+  this.socket.emit('webrtc-data', JSON.stringify(req));
+};
+
+/**
+ * Connection Manager
+ */
+
+var IS_CHROME = !!window.webkitRTCPeerConnection;
+var RTCPeerConnection;
+var RTCIceCandidate;
+var RTCSessionDescription;
+if (IS_CHROME) {
+  RTCPeerConnection = webkitRTCPeerConnection;
+  RTCIceCandidate = window.RTCIceCandidate;
+  RTCSessionDescription = window.RTCSessionDescription;
+} else {
+  RTCPeerConnection = mozRTCPeerConnection;
+  RTCIceCandidate = mozRTCIceCandidate;
+  RTCSessionDescription = mozRTCSessionDescription;
+}
+
+var CONFIGURATION = {
+  iceServers: [
+    {url: "stun:stun.l.google.com:19302"},
+    {url: "stun:stun1.l.google.com:19302"},
[…]

### 2015-05-02 src/fiddler/frontend.js
Remove unused code

@@ -1,209 +1,0 @@
-// -------------------------------------------------
-// WEBSOCKETS
-// -------------------------------------------------
-var socket = io("http://localhost:5000");
-var peers = [];
-var assetData = {};
-socket.on("connect", function(){
-  console.log("connected socket!");
-});
-socket.on("peer-reply", function(data) {
-  peers = data.peers;
-  console.log(data.peers);
-  var item = $("[data-zauberflote=" + data.hash + "]")[0];
-  if (data.peers.length ==  0) {  
-    insertImage(item, data.hash);
-  } else {
-    item.className = item.className + " waiting";
-    start();
-  }
-});
-socket.on("webrtc-data", function(data){
-  signalingChannel.onmessage(data);
-});
-socket.on("disconnect", function(){
-  console.log("disconnected socket");
-});
-
-
-
-// -------------------------------------------------
-// FRONTEND DOC ELEMENTS
-// -------------------------------------------------
-
-$(document).ready(function() {
-  // auto p2p
-  var p2pAssets = $(".zauberflote-item");
-  for (var i = 0; i < p2pAssets.length; i++) {
-    var hash = $(p2pAssets[i]).attr("data-zauberflote");
-    console.log("emitting " + hash);
-    socket.emit("peer-request",hash);
-  }
-});
-
-function insertImage(item, hash) {
-  var src = $(item).attr("data-original");
-  var xhr = new XMLHttpRequest();
-  // note: CORS must be enabled
-  xhr.open("GET", src, true);
-  xhr.responseType = "blob";
-  xhr.onload = function(d) {
-    if (this.status == 200) {
-      var blob = this.response;
-      console.log(blob);
-      item.onload = function(e) {
-        window.URL.revokeObjectURL(item.src); // cleanup
-      };
-      item.src = window.URL.createObjectURL(blob);
-      var reader = new window.FileReader();
-      reader.readAsDataURL(blob); 
-      reader.onloadend = function() {
-        base64data = reader.result;                
-        console.log(base64data );
-        assetData[hash] = base64data;
-      }
-      socket.emit("add", hash);
-    }
-  };
-  xhr.send();
-}
-
-
-
-// ------------------------------------------------
-// WEBRTC
-// ------------------------------------------------
-
-
-// CONFIGS
-var IS_CHROME = !!window.webkitRTCPeerConnection,
[…]

### 2015-05-02 src/fiddler/peerdl.js
Implement marshalling

@@ -27,7 +27,7 @@ function Tracker(socket) {
   this.counter = 0;
 }
 
-Tracker.prototype.getPeersForHash = function(hash, callback) {
+Tracker.prototype.getPeers = function(hash, callback) {
   var seq = ++this.counter;
   var req = {seq: seq, hash: hash};
   this.socket.emit('peer-request', JSON.stringify(req));
@@ -38,7 +38,7 @@ Tracker.prototype.getPeersForHash = function(hash, callback) {
   });
 };
 
-Tracker.prototype.addHash = function(hash) {
+Tracker.prototype.advertise = function(hash) {
   this.socket.emit('add', hash);
 };
 
@@ -190,7 +190,7 @@ ConnectionManager.prototype.reset = function(peer) {
 ConnectionManager.prototype.send = function(peer, data) {
   this.connect(peer);
   var dataChannel = this.dataChannels[peer];
-  if (typeof dataChannel === 'undefined' ||
+  if (typeof(dataChannel) === 'undefined' ||
       dataChannel === null ||
       dataChannel.readyState === 'closing' ||
       dataChannel.readyState === 'closed') {
@@ -204,11 +204,71 @@ ConnectionManager.prototype.send = function(peer, data) {
     var old = dataChannel.onopen;
     dataChannel.onopen = function(event) {
       dataChannel.send(data);
-      if (typeof old !== 'undefined' && old !== null) {
+      if (typeof(old) !== 'undefined' && old !== null) {
         old(event);
       }
     };
   }
+};
+
+/**
+ * Download Manager
+ */
+
+function marshalBuffer(buffer) {
+  var binary = '';
+  var bytes = new Uint8Array(buffer);
+  var len = bytes.byteLength;
+  for (var i = 0; i < len; i++) {
+    binary += String.fromCharCode(bytes[i]);
+  }
+  return window.btoa(binary);
+}
+
+function unmarshalBuffer(base64) {
+  var binaryString =  window.atob(base64);
+  var len = binaryString.length;
+  var bytes = new Uint8Array(len);
+  for (var i = 0; i < len; i++)        {
+    bytes[i] = binaryString.charCodeAt(i);
+  }
+  return bytes.buffer;
+}
+
+function marshal(message) {
+  // message expected to be JSONable except for the payload field
+  // which this function will handle marshalling
+  if (message.hasOwnProperty('payload') &&
[…]

### 2015-05-02 src/fiddler/main.go
Add support for tracker to track sizes of data

@@ -14,14 +14,21 @@ import (
 	"math/big"
 )
 
-type PeerRequest struct {
+type InfoRequest struct {
 	Seq  int    `json:"seq"`
 	Hash string `json:"hash"`
 }
 
-type PeerReply struct {
+type PublishRequest struct {
+	Hash string `json:"hash"`
+	Size int `json:"size"`
+	AddPeer bool `json:"addPeer"`
+}
+
+type InfoReply struct {
 	Hash  string   `json:"hash"`
 	Peers []PeerId `json:"peers"`
+	Size int `json:"size"`
 }
 
 type WebRTCRequest struct {
@@ -43,13 +50,38 @@ func main() {
 
 		so.On("add", func(hash string) {
 			log.Println("add:", hash)
-			tracker.Add(id, hash)
+			ok := tracker.Add(id, hash)
+			if !ok {
+				log.Println("add error, untracked?");
+			}
 		})
 
-		so.On("webrtc-data", func(hash string) {
-			log.Println("webrtc-data:", hash)
+		so.On("publish", func(data string) {
+			// XXX for debugging only
+			// For security, there shouldn't be a way for people to
+			// publish stuff through the client socket interface.
+			// Stuff to be tracked should be added through a config
+			// file or some external authenticated interface.
+			log.Println("publish:", data)
+			var request PublishRequest
+			err := json.Unmarshal([]byte(data), &request)
+			if err != nil {
+				log.Println("unmarshalling error")
+				return
+			}
+			ok := tracker.Publish(request.Hash, request.Size)
+			if !ok {
+				log.Println("error publishing, duplicate?")
+			}
+			if request.AddPeer {
+				tracker.Add(PeerId(so.Id()), request.Hash)
+			}
+		})
+
+		so.On("webrtc-data", func(data string) {
+			log.Println("webrtc-data:", data)
 			var request WebRTCRequest
-			err := json.Unmarshal([]byte(hash), &request)
+			err := json.Unmarshal([]byte(data), &request)
 			if err != nil {
 				log.Println("ERROR AAAH")
 			}
@@ -65,14 +97,15 @@ func main() {
 
 		so.On("peer-request", func(req string) {
 			log.Println("peer-request:", req)
-			var request PeerRequest
[…]

### 2015-05-02 src/fiddler/peerdl.js

@@ -27,19 +27,27 @@ function Tracker(socket) {
   this.counter = 0;
 }
 
-Tracker.prototype.getPeers = function(hash, callback) {
+Tracker.prototype.getInfo = function(hash, callback) {
   var seq = ++this.counter;
   var req = {seq: seq, hash: hash};
   this.socket.emit('peer-request', JSON.stringify(req));
   this.socket.once('peer-reply-' + seq, function(data) {
     if (data.hash === hash) {
-      callback(data.peers);
+      callback(data);
     }
   });
 };
 
 Tracker.prototype.advertise = function(hash) {
   this.socket.emit('add', hash);
+};
+
+Tracker.prototype.publish = function(hash, size, addPeer) {
+  if (typeof(addPeer) === 'undefined' || addPeer === null) {
+    addPeer = true;
+  }
+  var req = {hash: hash, size: size, addPeer: addPeer};
+  this.socket.emit('publish', JSON.stringify(req));
 };
 
 /**
@@ -268,7 +276,7 @@ DownloadManager.prototype.publish = function(hash, data) {
     return;
   }
   this.downloaded[hash] = data;
-  this.tracker.advertise(hash);
+  this.tracker.publish(hash, data.byteLength);
 };
 
 /**
@@ -279,14 +287,15 @@ DownloadManager.prototype.publish = function(hash, data) {
 
 var tracker = new Tracker(skt);
 var peer = [];
-tracker.getPeers('magic', function(peers) {
-  console.log(peers);
+tracker.getInfo('magic', function(info) {
+  console.log(info);
+  var peers = info.peers;
   if (peers.length > 0) {
     peer = peers[0];
   }
 });
-tracker.advertise('magic');
-tracker.getPeers('magic', function(peers) {
+tracker.publish('magic', 5);
+tracker.getInfo('magic', function(peers) {
   console.log(peers);
 });
 

### 2015-05-02 src/fiddler/peerdl.js
Implement DownloadManager

@@ -262,12 +262,33 @@ function unmarshal(data) {
 }
 
 function DownloadManager(tracker, connectionManager) {
+  var that = this;
   this.tracker = tracker;
   this.connectionManager = connectionManager;
   this.downloaded = {};
+  // the following implementation detail will probably change in order to
+  // improve performance, but the DownloadManager API should stay the same
+  this.pending = {}; // map from hash to callback function
   // handle request or response appropriately
   this.connectionManager.onmessage = function(peer, data) {
-    // TODO
+    console.log('cm onmessage ' + peer + ' ' + data);
+    var msg = unmarshal(data);
+    if (msg.type === 'request') {
+      var hash = msg.hash;
+      if (that.downloaded.hasOwnProperty(hash)) {
+        var resp = {type: 'data', hash: hash, payload: that.downloaded[hash]};
+        that.connectionManager.send(peer, marshal(resp));
+      }
+    } else if (msg.type === 'data') {
+      // handle data, call callback if necessary
+      var hash = msg.hash;
+      if (that.pending.hasOwnProperty(hash)) {
+        that.downloaded[hash] = msg.payload;
+        var callback = that.pending[hash];
+        delete that.pending[hash];
+        callback(that.downloaded[hash]);
+      }
+    }
   };
 }
 
@@ -279,40 +300,85 @@ DownloadManager.prototype.publish = function(hash, data) {
   this.tracker.publish(hash, data.byteLength);
 };
 
+// callback takes (ArrayBuffer, Error)
+function xhrGet(url, callback) {
+  // CORS needs to be enabled for this to work
+  // the server needs to send the Access-Control-Allow-Origin: *
+  // header
+  var xhr = new XMLHttpRequest();
+  xhr.open('GET', url, true);
+  xhr.responseType = 'arraybuffer';
+  xhr.onerror = function(e) {
+    callback(null, e);
+  };
+  xhr.onload = function(e) {
+    if (this.status == 200) {
+      var buffer = this.response;
+      callback(buffer);
+    } else {
+      callback(null, new Error('XHR returned ' + this.status));
+    }
+  };
+  xhr.send();
+}
+
+// callback takes (ArrayBuffer, Error)
+DownloadManager.prototype.download = function(hash, fallbackUrl, callback) {
+  var that = this;
+  this.tracker.getInfo(hash, function(info) {
+    if (info.peers.length > 0) {
[…]

### 2015-05-02 src/fiddler/peerdl.js
Make peer advertise on download

@@ -286,6 +286,7 @@ function DownloadManager(tracker, connectionManager) {
         that.downloaded[hash] = msg.payload;
         var callback = that.pending[hash];
         delete that.pending[hash];
+        that.tracker.advertise(hash);
         callback(that.downloaded[hash]);
       }
     }
@@ -325,6 +326,10 @@ function xhrGet(url, callback) {
 // callback takes (ArrayBuffer, Error)
 DownloadManager.prototype.download = function(hash, fallbackUrl, callback) {
   var that = this;
+  if (this.downloaded.hasOwnProperty(hash)) {
+    callback(this.downloaded[hash]);
+    return;
+  }
   this.tracker.getInfo(hash, function(info) {
     if (info.peers.length > 0) {
       // p2p download
@@ -339,6 +344,7 @@ DownloadManager.prototype.download = function(hash, fallbackUrl, callback) {
         xhrGet(fallbackUrl, function(data, err) {
           if (data !== null) {
             that.downloaded[hash] = data;
+            that.tracker.advertise(hash);
           }
           callback(data, err);
         });

### 2015-05-02 src/fiddler/peerdl.js
Remove debug print

@@ -271,7 +271,6 @@ function DownloadManager(tracker, connectionManager) {
   this.pending = {}; // map from hash to callback function
   // handle request or response appropriately
   this.connectionManager.onmessage = function(peer, data) {
-    console.log('cm onmessage ' + peer + ' ' + data);
     var msg = unmarshal(data);
     if (msg.type === 'request') {
       var hash = msg.hash;

### 2015-05-03 src/fiddler/peerdl.js
Reorganize

@@ -13,12 +13,6 @@ function logError(error) {
 }
 
 /**
- * Socket
- */
-
-var skt = io("http://localhost:5000");
-
-/**
  * Tracker Interface
  */
 
@@ -361,6 +355,7 @@ DownloadManager.prototype.download = function(hash, fallbackUrl, callback) {
  * This should be removed in a real build
  */
 
+var skt = io("http://localhost:5000");
 var tr = new Tracker(skt);
 var sc = new SignalingChannel(skt);
 var cm = new ConnectionManager(sc);

### 2015-05-03 src/fiddler/peerdl.js
Separate out code that interacts with the page

@@ -348,37 +348,3 @@ DownloadManager.prototype.download = function(hash, fallbackUrl, callback) {
     }
   });
 };
-
-/**
- * Testing code
- *
- * This should be removed in a real build
- */
-
-var skt = io("http://localhost:5000");
-var tr = new Tracker(skt);
-var sc = new SignalingChannel(skt);
-var cm = new ConnectionManager(sc);
-var dm = new DownloadManager(tr, cm);
-
-var ab = new ArrayBuffer(4);
-var v = new Uint8Array(ab);
-v[0] = 1; v[1] = 3; v[2] = 3; v[3] = 7;
-var msg = {type: 'data', start: 1337, payload: ab};
-
-function pub() {
-  dm.publish('test', ab);
-}
-
-function get() {
-  dm.download('test', null, function(data, err) {
-    if (err) {
-      console.log('error');
-      console.log(err);
-    } else {
-      console.log('got data!');
-      var v = new Uint8Array(data);
-      console.log(v);
-    }
-  });
-}

### 2015-05-03 src/fiddler/zauberflote.js

@@ -1,0 +1,35 @@
+/**
+ * Setup
+ */
+
+var skt = io("http://localhost:5000");
+var tr = new Tracker(skt);
+var sc = new SignalingChannel(skt);
+var cm = new ConnectionManager(sc);
+var dm = new DownloadManager(tr, cm);
+
+/**
+ * Testing code
+ */
+
+var ab = new ArrayBuffer(4);
+var v = new Uint8Array(ab);
+v[0] = 1; v[1] = 3; v[2] = 3; v[3] = 7;
+var msg = {type: 'data', start: 1337, payload: ab};
+
+function pub() {
+  dm.publish('test', ab);
+}
+
+function get() {
+  dm.download('test', null, function(data, err) {
+    if (err) {
+      console.log('error');
+      console.log(err);
+    } else {
+      console.log('got data!');
+      var v = new Uint8Array(data);
+      console.log(v);
+    }
+  });
+}

### 2015-05-03 src/fiddler/peerdl.js
Add peer-to-peer downloading functionality

@@ -286,12 +286,12 @@ function DownloadManager(tracker, connectionManager) {
   };
 }
 
-DownloadManager.prototype.publish = function(hash, data) {
+DownloadManager.prototype.publish = function(hash, data, addPeer) {
   if (this.downloaded.hasOwnProperty(hash)) {
     return;
   }
   this.downloaded[hash] = data;
-  this.tracker.publish(hash, data.byteLength);
+  this.tracker.publish(hash, data.byteLength, addPeer);
 };
 
 // callback takes (ArrayBuffer, Error)
@@ -325,6 +325,7 @@ DownloadManager.prototype.download = function(hash, fallbackUrl, callback) {
   }
   this.tracker.getInfo(hash, function(info) {
     if (info.peers.length > 0) {
+      console.log('downloading over p2p: ' + hash);
       // p2p download
       // TODO chunking, parallelization, hash validation, failure handling
       that.pending[hash] = callback;
@@ -332,6 +333,7 @@ DownloadManager.prototype.download = function(hash, fallbackUrl, callback) {
       var msg = {type: 'request', hash: hash};
       that.connectionManager.send(peer, marshal(msg));
     } else {
+      console.log('downloading over xhr: ' + hash);
       if (fallbackUrl !== null) {
         // download via xhr, fallback has to allow CORS
         xhrGet(fallbackUrl, function(data, err) {

### 2015-05-03 src/fiddler/zauberflote.js

@@ -2,34 +2,33 @@
  * Setup
  */
 
-var skt = io("http://localhost:5000");
+var skt = io('http://localhost:5000');
 var tr = new Tracker(skt);
 var sc = new SignalingChannel(skt);
 var cm = new ConnectionManager(sc);
 var dm = new DownloadManager(tr, cm);
 
 /**
- * Testing code
+ * Automatic p2p download
  */
 
-var ab = new ArrayBuffer(4);
-var v = new Uint8Array(ab);
-v[0] = 1; v[1] = 3; v[2] = 3; v[3] = 7;
-var msg = {type: 'data', start: 1337, payload: ab};
+$(document).ready(function() {
+  var p2pAssets = $('.zf-item');
+  for (var i = 0; i < p2pAssets.length; i++) {
+    var item = p2pAssets[i];
+    var hash = $(item).attr('data-zf-hash');
+    var fallback = $(item).attr('data-zf-fallback');
+    dm.download(hash, fallback, function(data, err) {
+      // XXX this only works for images
 
-function pub() {
-  dm.publish('test', ab);
-}
-
-function get() {
-  dm.download('test', null, function(data, err) {
-    if (err) {
-      console.log('error');
-      console.log(err);
-    } else {
-      console.log('got data!');
-      var v = new Uint8Array(data);
-      console.log(v);
-    }
-  });
-}
+      // perhaps we should store the content type in the tracker as well,
+      // instead of just setting it to 'application/octet-stream' and letting
+      // the browser deal with it
+      var blob = new Blob([data], {type: 'application/octet-stream'});
+      item.onload = function(e) {
+        window.URL.revokeObjectURL(item.src); // cleanup
+      };
+      item.src = window.URL.createObjectURL(blob);
+    });
+  }
+});

### 2015-05-03 src/fiddler/peerdl.js
Remove unneeded class

@@ -4,11 +4,17 @@
  * Utilities
  */
 
-var DEBUG = false;
+var DEBUG = true;
 
 function logError(error) {
   if (DEBUG) {
     console.log('error: ' + error);
+  }
+}
+
+function trace(msg) {
+  if (DEBUG) {
+    console.log(msg);
   }
 }
 
@@ -325,7 +331,7 @@ DownloadManager.prototype.download = function(hash, fallbackUrl, callback) {
   }
   this.tracker.getInfo(hash, function(info) {
     if (info.peers.length > 0) {
-      console.log('downloading over p2p: ' + hash);
+      trace('downloading over p2p: ' + hash);
       // p2p download
       // TODO chunking, parallelization, hash validation, failure handling
       that.pending[hash] = callback;
@@ -333,7 +339,7 @@ DownloadManager.prototype.download = function(hash, fallbackUrl, callback) {
       var msg = {type: 'request', hash: hash};
       that.connectionManager.send(peer, marshal(msg));
     } else {
-      console.log('downloading over xhr: ' + hash);
+      trace('downloading over xhr: ' + hash);
       if (fallbackUrl !== null) {
         // download via xhr, fallback has to allow CORS
         xhrGet(fallbackUrl, function(data, err) {

### 2015-05-03 src/fiddler/zauberflote.js

@@ -13,7 +13,7 @@ var dm = new DownloadManager(tr, cm);
  */
 
 $(document).ready(function() {
-  var p2pAssets = $('.zf-item');
+  var p2pAssets = $('[data-zf-hash]');
   for (var i = 0; i < p2pAssets.length; i++) {
     var item = p2pAssets[i];
     var hash = $(item).attr('data-zf-hash');

### 2015-05-03 src/fiddler/zauberflote.js
Refine find

@@ -13,14 +13,13 @@ var dm = new DownloadManager(tr, cm);
  */
 
 $(document).ready(function() {
-  var p2pAssets = $('[data-zf-hash]');
+  // XXX this is only implemented for images
+  var p2pAssets = $('img[data-zf-hash]');
   for (var i = 0; i < p2pAssets.length; i++) {
     var item = p2pAssets[i];
     var hash = $(item).attr('data-zf-hash');
     var fallback = $(item).attr('data-zf-fallback');
     dm.download(hash, fallback, function(data, err) {
-      // XXX this only works for images
-
       // perhaps we should store the content type in the tracker as well,
       // instead of just setting it to 'application/octet-stream' and letting
       // the browser deal with it

### 2015-05-03 src/fiddler/zauberflote.js
WIP script and link tag support

@@ -1,3 +1,4 @@
+"use strict";
 /**
  * Setup
  */
@@ -13,21 +14,41 @@ var dm = new DownloadManager(tr, cm);
  */
 
 $(document).ready(function() {
-  // XXX this is only implemented for images
-  var p2pAssets = $('img[data-zf-hash]');
+  var p2pAssets = $('[data-zf-hash]');
   for (var i = 0; i < p2pAssets.length; i++) {
     var item = p2pAssets[i];
     var hash = $(item).attr('data-zf-hash');
     var fallback = $(item).attr('data-zf-fallback');
+    var derp = 0;
+    // XXX it seems that the download manager doesn't always call this callback
+    // and/or calls it multiple times
     dm.download(hash, fallback, function(data, err) {
       // perhaps we should store the content type in the tracker as well,
       // instead of just setting it to 'application/octet-stream' and letting
       // the browser deal with it
-      var blob = new Blob([data], {type: 'application/octet-stream'});
-      item.onload = function(e) {
-        window.URL.revokeObjectURL(item.src); // cleanup
-      };
-      item.src = window.URL.createObjectURL(blob);
-    });
+      var blob;
+
+      switch(item.tagName) {
+        case 'IMG': // we could just delete this and use the default handler
+          console.log("downloading img");
+          blob = new Blob([data], {type: 'application/octet-stream'});
+          item.src = window.URL.createObjectURL(blob);
+          break;
+        case 'SCRIPT':
+          console.log("downloading script");
+          blob = new Blob([data], {type: 'text/javascript'});
+          item.src = window.URL.createObjectURL(blob);
+          break;
+        case 'LINK':
+          console.log("downloading css");
+          blob = new Blob([data], {type: 'text/css'});
+          item.rel = "stylesheet";
+          item.href = window.URL.createObjectURL(blob);
+          break;
+        default:
+          blob = new Blob([data], {type: 'application/octet-stream'});
+          item.src = window.URL.createObjectURL(blob);
+      }
+      });
   }
 });

### 2015-05-03 src/fiddler/peerdl.js
sketched out DownloadObject class

@@ -261,6 +261,37 @@ function unmarshal(data) {
   return message;
 }
 
+// Download object -- data representation of file chunks
+function DownloadObject(hash, callback) {
+  // that.pending[hash] = callback;
+  // var peer = info.peers[0]; // just choose one for now
+  // var msg = {type: 'request', hash: hash};
+  // that.connectionManager.send(peer, marshal(msg));
+  
+  // chunk download
+  
+  
+}
+
+// Start the download
+DownloadObject.prototype.get() {
+  var done = false;
+  while (!done) {
+    done = true;
+    // loop through chunks
+    for(chunk in this.chunks) {
+      // once every 20x loops, refresh tracker peer info
+      // check if timeout reached
+      // increment number times asked
+      // ask random other peer for chunk
+    }
+  }
+}
+
+// Chunk of download obj received
+DownloadObject.prototype.receive(payload) {
+}
+
 function DownloadManager(tracker, connectionManager) {
   var that = this;
   this.tracker = tracker;
@@ -268,7 +299,7 @@ function DownloadManager(tracker, connectionManager) {
   this.downloaded = {};
   // the following implementation detail will probably change in order to
   // improve performance, but the DownloadManager API should stay the same
-  this.pending = {}; // map from hash to callback function
+  this.pending = {}; // map from hash to DownloadObjects
   // handle request or response appropriately
   this.connectionManager.onmessage = function(peer, data) {
     var msg = unmarshal(data);
@@ -282,11 +313,14 @@ function DownloadManager(tracker, connectionManager) {
       // handle data, call callback if necessary
       var hash = msg.hash;
       if (that.pending.hasOwnProperty(hash)) {
-        that.downloaded[hash] = msg.payload;
-        var callback = that.pending[hash];
-        delete that.pending[hash];
-        that.tracker.advertise(hash);
-        callback(that.downloaded[hash]);
+        // XXX delete
+        // that.downloaded[hash] = msg.payload;
+        var downloadObject = that.pending[hash];
+        // TODO implement finished downloading object code--delete, advertise, callback
+        // delete that.pending[hash];
+        downloadObject.receive(msg.payload);
+        // that.tracker.advertise(hash);
+        // callback(that.downloaded[hash]);
       }
     }
   };
@@ -334,10 +368,14 @@ DownloadManager.prototype.download = function(hash, fallbackUrl, callback) {
       trace('downloading over p2p: ' + hash);
       // p2p download
[…]

### 2015-05-03 src/fiddler/peerdl.js
download object sans finish/cleanup done

@@ -262,34 +262,74 @@ function unmarshal(data) {
 }
 
 // Download object -- data representation of file chunks
-function DownloadObject(hash, callback) {
-  // that.pending[hash] = callback;
-  // var peer = info.peers[0]; // just choose one for now
-  // var msg = {type: 'request', hash: hash};
-  // that.connectionManager.send(peer, marshal(msg));
+function DownloadObject(connectionManager, peers, size, hash, callback) {
+  this.connectionManager = connectionManager;
+  this.peers = peers;
+  this.downloadSize = size;
+  this.hash = hash;
+  this.done = callback;
+  this.chunkSize = 1000; // 1KB chunks
   
-  // chunk download
-  
-  
+
+  // instantiate chunk array
+  this.chunks = [];
+  for (var i = 0; i < this.downloadSize; i += this.chunkSize) {
+    this.chunks.push({seq: i, peer: null, lastSent: null, numTries: 0, data: null});
+  }
 }
 
 // Start the download
 DownloadObject.prototype.get() {
   var done = false;
+  var loopCount = 0;
   while (!done) {
     done = true;
+    // once every 20x loops, refresh tracker peer info
+    loopCount = loopCount + 1;
+    if (loopCount % 20 == 0) {
+      // TODO(refresh)
+    }
     // loop through chunks
     for(chunk in this.chunks) {
-      // once every 20x loops, refresh tracker peer info
-      // check if timeout reached
-      // increment number times asked
-      // ask random other peer for chunk
+      // chunk.lastSent is in milliseconds
+      if (this.timedOut(chunk.lastSent, chunk.numTries)) {
+        var peer = this.choosePeer();
+        var msg = {type: 'request', hash: this.hash, chunkSeq: chunk.seq};
+        this.connectionManager.send(peer, marshal(msg));
+        // update chunk data
+        chunk.peer = peer;
+        var now = new Date();
+        chunk.lastSent = now.getTime();
+        chunk.numTries = chunk.numTries + 1;
+      }
     }
   }
+  this.finish();
+}
+
+DownloadObject.prototype.timedOut(lastSent, numTries) {
+  var now = new Date();
+  if (lastSent == null || now.getTime() - lastSent > timeoutCutoff) {
+    return true;
+  }
+  return false;
+}
+
+DownloadObject.prototype.choosePeer() {
+  return this.peers[Math.floor(Math.random() * this.peers.length)];
 }
 
 // Chunk of download obj received
-DownloadObject.prototype.receive(payload) {
[…]

### 2015-05-03 src/fiddler/zauberflote.js
Fix bug with scope
Because of the way Javascript scoping works, the callbacks that are
created in a loop will all refer to the same item. This can be fixed by
wrapping in an IIFE.

@@ -20,35 +20,35 @@ $(document).ready(function() {
     var hash = $(item).attr('data-zf-hash');
     var fallback = $(item).attr('data-zf-fallback');
     var derp = 0;
-    // XXX it seems that the download manager doesn't always call this callback
-    // and/or calls it multiple times
-    dm.download(hash, fallback, function(data, err) {
-      // perhaps we should store the content type in the tracker as well,
-      // instead of just setting it to 'application/octet-stream' and letting
-      // the browser deal with it
-      var blob;
+    (function(item) {
+      dm.download(hash, fallback, function(data, err) {
+        // perhaps we should store the content type in the tracker as well,
+        // instead of just setting it to 'application/octet-stream' and letting
+        // the browser deal with it
+        var blob;
 
-      switch(item.tagName) {
-        case 'IMG': // we could just delete this and use the default handler
-          console.log("downloading img");
-          blob = new Blob([data], {type: 'application/octet-stream'});
-          item.src = window.URL.createObjectURL(blob);
-          break;
-        case 'SCRIPT':
-          console.log("downloading script");
-          blob = new Blob([data], {type: 'text/javascript'});
-          item.src = window.URL.createObjectURL(blob);
-          break;
-        case 'LINK':
-          console.log("downloading css");
-          blob = new Blob([data], {type: 'text/css'});
-          item.rel = "stylesheet";
-          item.href = window.URL.createObjectURL(blob);
-          break;
-        default:
-          blob = new Blob([data], {type: 'application/octet-stream'});
-          item.src = window.URL.createObjectURL(blob);
-      }
+        switch(item.tagName) {
+          case 'IMG': // we could just delete this and use the default handler
+            console.log("downloading img");
+            blob = new Blob([data], {type: 'application/octet-stream'});
+            item.src = window.URL.createObjectURL(blob);
+            break;
+          case 'SCRIPT':
+            console.log("downloading script");
+            blob = new Blob([data], {type: 'text/javascript'});
+            item.src = window.URL.createObjectURL(blob);
+            break;
+          case 'LINK':
+            console.log("downloading css");
+            blob = new Blob([data], {type: 'text/css'});
+            item.rel = "stylesheet";
+            item.href = window.URL.createObjectURL(blob);
+            break;
+          default:
+            blob = new Blob([data], {type: 'application/octet-stream'});
+            item.src = window.URL.createObjectURL(blob);
+        }
       });
+    }(item));
   }
 });

### 2015-05-03 src/fiddler/peerdl.js
download object finished implemented

@@ -262,8 +262,8 @@ function unmarshal(data) {
 }
 
 // Download object -- data representation of file chunks
-function DownloadObject(connectionManager, peers, size, hash, callback) {
-  this.connectionManager = connectionManager;
+function DownloadObject(downloadManager, peers, size, hash, callback) {
+  this.downloadManager = downloadManager;
   this.peers = peers;
   this.downloadSize = size;
   this.hash = hash;
@@ -274,7 +274,7 @@ function DownloadObject(connectionManager, peers, size, hash, callback) {
   // instantiate chunk array
   this.chunks = [];
   for (var i = 0; i < this.downloadSize; i += this.chunkSize) {
-    this.chunks.push({seq: i, peer: null, lastSent: null, numTries: 0, data: null});
+    this.chunks.push({peer: null, lastSent: null, numTries: 0, data: null});
   }
 }
 
@@ -283,24 +283,31 @@ DownloadObject.prototype.get() {
   var done = false;
   var loopCount = 0;
   while (!done) {
-    done = true;
-    // once every 20x loops, refresh tracker peer info
+    done = true; // will be set to false if any chunk not downloaded
+    // once every 100x loops, refresh tracker peer info
     loopCount = loopCount + 1;
-    if (loopCount % 20 == 0) {
-      // TODO(refresh)
+    if (loopCount % 100 == 0) {
+      this.tracker.getInfo(hash, function(info) {
+        this.peers = info.peers;
+      }
     }
     // loop through chunks
-    for(chunk in this.chunks) {
+    for(var i = 0; i < this.chunks.length; i++) {
+      var chunk = this.chunks[i];
       // chunk.lastSent is in milliseconds
-      if (this.timedOut(chunk.lastSent, chunk.numTries)) {
-        var peer = this.choosePeer();
-        var msg = {type: 'request', hash: this.hash, chunkSeq: chunk.seq};
-        this.connectionManager.send(peer, marshal(msg));
-        // update chunk data
-        chunk.peer = peer;
-        var now = new Date();
-        chunk.lastSent = now.getTime();
-        chunk.numTries = chunk.numTries + 1;
+      if (chunk.data == null) {
+        if (this.timedOut(chunk.lastSent, chunk.numTries)) {
+          var peer = this.choosePeer();
+          // TODO(add chunk seq to protocol)
+          var msg = {type: 'request', hash: this.hash, seq: i};
+          this.downloadManager.connectionManager.send(peer, marshal(msg));
+          // update chunk data
[…]

### 2015-05-03 src/fiddler/peerdl.js
implemented download chunking

@@ -268,12 +268,10 @@ function DownloadObject(downloadManager, peers, size, hash, callback) {
   this.downloadSize = size;
   this.hash = hash;
   this.done = callback;
-  this.chunkSize = 1000; // 1KB chunks
-  
 
   // instantiate chunk array
   this.chunks = [];
-  for (var i = 0; i < this.downloadSize; i += this.chunkSize) {
+  for (var i = 0; i < this.downloadSize; i += this.downloadManager.chunkSize) {
     this.chunks.push({peer: null, lastSent: null, numTries: 0, data: null});
   }
 }
@@ -315,6 +313,7 @@ DownloadObject.prototype.get() {
 }
 
 DownloadObject.prototype.timedOut(lastSent, numTries) {
+  var timeoutCutoff = 100; // 100 ms
   var now = new Date();
   if (lastSent == null || now.getTime() - lastSent > timeoutCutoff) {
     return true;
@@ -327,14 +326,16 @@ DownloadObject.prototype.choosePeer() {
 }
 
 // Chunk of download obj received
-DownloadObject.prototype.received(payload) {
-  this.chunks[payload.seq].data = msg.payload;
+DownloadObject.prototype.received(seq, payload) {
+  this.chunks[seq].data = payload;
 }
 
 DownloadObject.prototype.finish() {
-  var content = "";
+  var content = new ArrayBuffer(this.downloadSize);
   for (var i = 0; i < this.chunks.length; i++) {
-    content += this.chunks[i].data;
+    var chunkSize = this.downloadManager.chunkSize;
+    var view = new Uint8Array(content, i * chunkSize, chunkSize);
+    view.set(new Uint8Array(this.chunks[i].data));
   }
   this.downloadManager.finishDownload(this.hash, content, this.callback);
 }
@@ -344,6 +345,7 @@ function DownloadManager(tracker, connectionManager) {
   this.tracker = tracker;
   this.connectionManager = connectionManager;
   this.downloaded = {};
+  this.chunkSize = 1000; // 1KB chunk size
   // the following implementation detail will probably change in order to
   // improve performance, but the DownloadManager API should stay the same
   this.pending = {}; // map from hash to DownloadObjects
@@ -353,7 +355,8 @@ function DownloadManager(tracker, connectionManager) {
     if (msg.type === 'request') {
       var hash = msg.hash;
       if (that.downloaded.hasOwnProperty(hash)) {
[…]

### 2015-05-03 src/fiddler/peerdl.js
bug fixing

@@ -277,7 +277,7 @@ function DownloadObject(downloadManager, peers, size, hash, callback) {
 }
 
 // Start the download
-DownloadObject.prototype.get() {
+DownloadObject.prototype.get = function() {
   var done = false;
   var loopCount = 0;
   while (!done) {
@@ -287,7 +287,7 @@ DownloadObject.prototype.get() {
     if (loopCount % 100 == 0) {
       this.tracker.getInfo(hash, function(info) {
         this.peers = info.peers;
-      }
+      });
     }
     // loop through chunks
     for(var i = 0; i < this.chunks.length; i++) {
@@ -312,7 +312,7 @@ DownloadObject.prototype.get() {
   this.finish();
 }
 
-DownloadObject.prototype.timedOut(lastSent, numTries) {
+DownloadObject.prototype.timedOut = function(lastSent, numTries) {
   var timeoutCutoff = 100; // 100 ms
   var now = new Date();
   if (lastSent == null || now.getTime() - lastSent > timeoutCutoff) {
@@ -321,23 +321,23 @@ DownloadObject.prototype.timedOut(lastSent, numTries) {
   return false;
 }
 
-DownloadObject.prototype.choosePeer() {
+DownloadObject.prototype.choosePeer = function() {
   return this.peers[Math.floor(Math.random() * this.peers.length)];
 }
 
 // Chunk of download obj received
-DownloadObject.prototype.received(seq, payload) {
+DownloadObject.prototype.received = function(seq, payload) {
   this.chunks[seq].data = payload;
 }
 
-DownloadObject.prototype.finish() {
+DownloadObject.prototype.finish = function() {
   var content = new ArrayBuffer(this.downloadSize);
   for (var i = 0; i < this.chunks.length; i++) {
     var chunkSize = this.downloadManager.chunkSize;
     var view = new Uint8Array(content, i * chunkSize, chunkSize);
     view.set(new Uint8Array(this.chunks[i].data));
   }
-  this.downloadManager.finishDownload(this.hash, content, this.callback);
+  this.downloadManager.finishDownload(this.hash, content, this.done);
 }
 
 function DownloadManager(tracker, connectionManager) {
@@ -424,7 +424,7 @@ DownloadManager.prototype.download = function(hash, fallbackUrl, callback) {
       // var peer = info.peers[0]; // just choose one for now
       // var msg = {type: 'request', hash: hash};
       // that.connectionManager.send(peer, marshal(msg));
[…]

### 2015-05-03 src/fiddler/zauberflote.js

@@ -22,6 +22,7 @@ $(document).ready(function() {
     var derp = 0;
     (function(item) {
       dm.download(hash, fallback, function(data, err) {
+        console.log(new Uint8Array(data));
         // perhaps we should store the content type in the tracker as well,
         // instead of just setting it to 'application/octet-stream' and letting
         // the browser deal with it

### 2015-05-03 src/fiddler/peerdl.js
Fix busy loop

@@ -262,7 +262,7 @@ function unmarshal(data) {
 }
 
 // Download object -- data representation of file chunks
-function DownloadObject(downloadManager, peers, size, hash, callback) {
+function Download(downloadManager, peers, size, hash, callback) {
   this.downloadManager = downloadManager;
   this.peers = peers;
   this.downloadSize = size;
@@ -277,28 +277,33 @@ function DownloadObject(downloadManager, peers, size, hash, callback) {
 }
 
 // Start the download
-DownloadObject.prototype.get = function() {
-  var done = false;
+Download.prototype.start = function() {
+  var loopTickDuration = 30; // in ms
   var loopCount = 0;
-  while (!done) {
-    done = true; // will be set to false if any chunk not downloaded
+
+  var that = this;
+  var check = function() {
+    var done = true; // will be set to false if any chunk not downloaded
     // once every 100x loops, refresh tracker peer info
     loopCount = loopCount + 1;
     if (loopCount % 100 == 0) {
-      this.tracker.getInfo(hash, function(info) {
-        this.peers = info.peers;
+      that.tracker.getInfo(hash, function(info) {
+        that.peers = info.peers;
       });
     }
     // loop through chunks
-    for(var i = 0; i < this.chunks.length; i++) {
-      var chunk = this.chunks[i];
+    for(var i = 0; i < that.chunks.length; i++) {
+      var chunk = that.chunks[i];
       console.log("chunk: " + chunk.toString);
       // chunk.lastSent is in milliseconds
       if (chunk.data == null) {
-        if (this.timedOut(chunk.lastSent, chunk.numTries)) {
-          var peer = this.choosePeer();
-          var msg = {type: 'request', hash: this.hash, seq: i};
-          this.downloadManager.connectionManager.send(peer, marshal(msg));
+        if (that.timedOut(chunk.lastSent, chunk.numTries)) {
+          var peer = that.choosePeer();
+          var msg = {type: 'request', hash: that.hash, seq: i};
+          that.downloadManager.connectionManager.send(peer, marshal(msg));
+          // update chunk data
+          chunk.peer = peer;
+          var now = new Date();
           // update chunk data
           chunk.peer = peer;
           var now = new Date();
@@ -308,11 +313,17 @@ DownloadObject.prototype.get = function() {
         done = false;
       }
     }
-  }
-  this.finish();
+
+    if (!done) {
+      setTimeout(check, loopTickDuration);
+    } else {
[…]

### 2015-05-03 src/fiddler/peerdl.js
handle end of arraybuffer edge case

@@ -292,11 +292,11 @@ DownloadObject.prototype.get = function() {
     // loop through chunks
     for(var i = 0; i < this.chunks.length; i++) {
       var chunk = this.chunks[i];
+      console.log("chunk: " + chunk.toString);
       // chunk.lastSent is in milliseconds
       if (chunk.data == null) {
         if (this.timedOut(chunk.lastSent, chunk.numTries)) {
           var peer = this.choosePeer();
-          // TODO(add chunk seq to protocol)
           var msg = {type: 'request', hash: this.hash, seq: i};
           this.downloadManager.connectionManager.send(peer, marshal(msg));
           // update chunk data
@@ -334,7 +334,9 @@ DownloadObject.prototype.finish = function() {
   var content = new ArrayBuffer(this.downloadSize);
   for (var i = 0; i < this.chunks.length; i++) {
     var chunkSize = this.downloadManager.chunkSize;
-    var view = new Uint8Array(content, i * chunkSize, chunkSize);
+    var chunkStart = i * chunkSize;
+    var currChunkSize = Math.min(chunkStart + chunkSize, this.downloadSize) - chunkStart;
+    var view = new Uint8Array(content, chunkStart, currChunkSize);
     view.set(new Uint8Array(this.chunks[i].data));
   }
   this.downloadManager.finishDownload(this.hash, content, this.done);

### 2015-05-03 src/fiddler/zauberflote.js

@@ -19,10 +19,8 @@ $(document).ready(function() {
     var item = p2pAssets[i];
     var hash = $(item).attr('data-zf-hash');
     var fallback = $(item).attr('data-zf-fallback');
-    var derp = 0;
     (function(item) {
       dm.download(hash, fallback, function(data, err) {
-        console.log(new Uint8Array(data));
         // perhaps we should store the content type in the tracker as well,
         // instead of just setting it to 'application/octet-stream' and letting
         // the browser deal with it

### 2015-05-03 src/fiddler/peerdl.js
fixing p2p chunking bug

@@ -294,7 +294,7 @@ Download.prototype.start = function() {
     // loop through chunks
     for(var i = 0; i < that.chunks.length; i++) {
       var chunk = that.chunks[i];
-      console.log("chunk: " + chunk.toString);
+      // console.log(chunk);
       // chunk.lastSent is in milliseconds
       if (chunk.data == null) {
         if (that.timedOut(chunk.lastSent, chunk.numTries)) {
@@ -368,7 +368,12 @@ function DownloadManager(tracker, connectionManager) {
     if (msg.type === 'request') {
       var hash = msg.hash;
       if (that.downloaded.hasOwnProperty(hash)) {
-        var chunkData = that.downloaded[hash].slice(msg.seq * chunkSize, (msg.seq + 1) * chunkSize);
+        var chunkStart = msg.seq * that.chunkSize;
+        var currChunkSize = Math.min(chunkStart + that.chunkSize, that.downloaded[hash].byteLength) - chunkStart;
+        console.log(that.downloaded[hash]);
+        var chunkData = that.downloaded[hash].slice(chunkStart, currChunkSize);
+        console.log("sending data");
+        console.log(new Uint8Array(chunkData));
         var resp = {type: 'data', hash: hash, payload: chunkData, seq: msg.seq};
         that.connectionManager.send(peer, marshal(resp));
       }
@@ -447,6 +452,7 @@ DownloadManager.prototype.download = function(hash, fallbackUrl, callback) {
         xhrGet(fallbackUrl, function(data, err) {
           if (data !== null) {
             that.downloaded[hash] = data;
+            console.log(new Uint8Array(data));
             that.tracker.advertise(hash);
           }
           callback(data, err);

### 2015-05-03 src/fiddler/peerdl.js
Fix bug

@@ -294,7 +294,6 @@ Download.prototype.start = function() {
     // loop through chunks
     for(var i = 0; i < that.chunks.length; i++) {
       var chunk = that.chunks[i];
-      // console.log(chunk);
       // chunk.lastSent is in milliseconds
       if (chunk.data == null) {
         if (that.timedOut(chunk.lastSent, chunk.numTries)) {
@@ -369,11 +368,8 @@ function DownloadManager(tracker, connectionManager) {
       var hash = msg.hash;
       if (that.downloaded.hasOwnProperty(hash)) {
         var chunkStart = msg.seq * that.chunkSize;
-        var currChunkSize = Math.min(chunkStart + that.chunkSize, that.downloaded[hash].byteLength) - chunkStart;
-        console.log(that.downloaded[hash]);
+        var currChunkSize = Math.min(chunkStart + that.chunkSize, that.downloaded[hash].byteLength);
         var chunkData = that.downloaded[hash].slice(chunkStart, currChunkSize);
-        console.log("sending data");
-        console.log(new Uint8Array(chunkData));
         var resp = {type: 'data', hash: hash, payload: chunkData, seq: msg.seq};
         that.connectionManager.send(peer, marshal(resp));
       }
@@ -452,7 +448,6 @@ DownloadManager.prototype.download = function(hash, fallbackUrl, callback) {
         xhrGet(fallbackUrl, function(data, err) {
           if (data !== null) {
             that.downloaded[hash] = data;
-            console.log(new Uint8Array(data));
             that.tracker.advertise(hash);
           }
           callback(data, err);

### 2015-05-03 src/fiddler/peerdl.js
Add failover to HTTP

@@ -262,11 +262,12 @@ function unmarshal(data) {
 }
 
 // Download object -- data representation of file chunks
-function Download(downloadManager, peers, size, hash, callback) {
+function Download(downloadManager, peers, size, hash, fallbackUrl, callback) {
   this.downloadManager = downloadManager;
   this.peers = peers;
   this.downloadSize = size;
   this.hash = hash;
+  this.fallbackUrl = fallbackUrl;
   this.done = callback;
 
   // instantiate chunk array
@@ -278,7 +279,8 @@ function Download(downloadManager, peers, size, hash, callback) {
 
 // Start the download
 Download.prototype.start = function() {
-  var loopTickDuration = 30; // in ms
+  var loopTickDuration = 25; // in ms
+  var trackerCheckSkip = 10;
   var loopCount = 0;
 
   var that = this;
@@ -286,10 +288,16 @@ Download.prototype.start = function() {
     var done = true; // will be set to false if any chunk not downloaded
     // once every 100x loops, refresh tracker peer info
     loopCount = loopCount + 1;
-    if (loopCount % 100 == 0) {
-      that.tracker.getInfo(hash, function(info) {
-        that.peers = info.peers;
+    if (loopCount % trackerCheckSkip == 0) {
+      loopCount = 0;
+      that.downloadManager.tracker.getInfo(that.hash, function(info) {
+        that.peers = info.peers || [];
       });
+    }
+    // fall back to HTTP?
+    if (that.peers.length == 0) {
+      that.abort();
+      return;
     }
     // loop through chunks
     for(var i = 0; i < that.chunks.length; i++) {
@@ -349,15 +357,28 @@ Download.prototype.finish = function() {
     var view = new Uint8Array(content, chunkStart, currChunkSize);
     view.set(new Uint8Array(this.chunks[i].data));
   }
-  this.downloadManager.finishDownload(this.hash, content, this.done);
+  this.downloadManager.finishDownload(this.hash, content, null, this.done);
 }
+
+Download.prototype.abort = function() {
+  trace('aborted ' + this.hash);
+  var that = this;
+  if (this.fallbackUrl !== null) {
+    xhrGet(this.fallbackUrl, function(data, err) {
+      that.downloadManager.finishDownload(that.hash, data, err, that.done);
+    });
+  } else {
+    var err = new Error('P2P download unavailable, no fallback provided');
+    that.downloadManager.finishDownload(that.hash, null, err, that.done);
+  }
+};
 
[…]

### 2015-05-03 src/fiddler/peerdl.js
Remove comment

@@ -286,7 +286,6 @@ Download.prototype.start = function() {
   var that = this;
   var check = function() {
     var done = true; // will be set to false if any chunk not downloaded
-    // once every 100x loops, refresh tracker peer info
     loopCount = loopCount + 1;
     if (loopCount % trackerCheckSkip == 0) {
       loopCount = 0;

### 2015-05-03 src/fiddler/peerdl.js
Update comments

@@ -452,19 +452,13 @@ DownloadManager.prototype.download = function(hash, fallbackUrl, callback) {
     callback(this.downloaded[hash]);
     return;
   } else if (this.pending.hasOwnProperty(hash)) {
-    // in progress, quit
+    // in progress, no need to do anything
     return;
   }
   this.tracker.getInfo(hash, function(info) {
     if (info.peers.length > 0) {
       trace('downloading over p2p: ' + hash);
-      // p2p download
-      // TODO chunking, parallelization, hash validation, failure handling
-      // XXX remove
-      // that.pending[hash] = callback;
-      // var peer = info.peers[0]; // just choose one for now
-      // var msg = {type: 'request', hash: hash};
-      // that.connectionManager.send(peer, marshal(msg));
+      // TODO hash validation
       var download = new Download(that, info.peers, info.size, hash, fallbackUrl, callback);
       that.pending[hash] = download;
       download.start();

### 2015-05-03 src/fiddler/peerdl.js
Enable more tests

@@ -44,7 +44,7 @@ Tracker.prototype.advertise = function(hash) {
 
 Tracker.prototype.publish = function(hash, size, addPeer) {
   if (typeof(addPeer) === 'undefined' || addPeer === null) {
-    addPeer = true;
+    addPeer = false;
   }
   var req = {hash: hash, size: size, addPeer: addPeer};
   this.socket.emit('publish', JSON.stringify(req));

### 2015-05-04 src/fiddler/peerdl.js
Add hash checking

@@ -356,7 +356,14 @@ Download.prototype.finish = function() {
     var view = new Uint8Array(content, chunkStart, currChunkSize);
     view.set(new Uint8Array(this.chunks[i].data));
   }
-  this.downloadManager.finishDownload(this.hash, content, null, this.done);
+  // validate hash
+  if (this.downloadManager.hashfn(content) !== this.hash) {
+    trace('hash mismatch for ' + this.hash + ', falling back');
+    this.abort();
+  } else {
+    trace('hash ok for ' + this.hash);
+    this.downloadManager.finishDownload(this.hash, content, null, this.done);
+  }
 }
 
 Download.prototype.abort = function() {
@@ -372,10 +379,11 @@ Download.prototype.abort = function() {
   }
 };
 
-function DownloadManager(tracker, connectionManager) {
+function DownloadManager(tracker, connectionManager, hashfn) {
   var that = this;
   this.tracker = tracker;
   this.connectionManager = connectionManager;
+  this.hashfn = hashfn;
   this.downloaded = {};
   this.chunkSize = 1024; // 1KB chunk size
   // the following implementation detail will probably change in order to
@@ -456,27 +464,8 @@ DownloadManager.prototype.download = function(hash, fallbackUrl, callback) {
     return;
   }
   this.tracker.getInfo(hash, function(info) {
-    if (info.peers.length > 0) {
-      trace('downloading over p2p: ' + hash);
-      // TODO hash validation
-      var download = new Download(that, info.peers, info.size, hash, fallbackUrl, callback);
-      that.pending[hash] = download;
-      download.start();
-    } else {
-      trace('downloading over xhr: ' + hash);
-      if (fallbackUrl !== null) {
-        // download via xhr, fallback has to allow CORS
-        xhrGet(fallbackUrl, function(data, err) {
-          if (data !== null) {
-            that.downloaded[hash] = data;
-            that.tracker.advertise(hash);
-          }
-          callback(data, err);
-        });
-      } else {
-        var err = new Error('P2P download unavailable, no fallback provided');
-        callback(null, err);
-      }
-    }
+    var download = new Download(that, info.peers, info.size, hash, fallbackUrl, callback);
+    that.pending[hash] = download;
+    download.start();
   });
 };

### 2015-05-04 src/fiddler/zauberflote.js

@@ -7,7 +7,7 @@ var skt = io('http://localhost:5000');
 var tr = new Tracker(skt);
 var sc = new SignalingChannel(skt);
 var cm = new ConnectionManager(sc);
-var dm = new DownloadManager(tr, cm);
+var dm = new DownloadManager(tr, cm, sha1.hash);
 
 /**
  * Automatic p2p download

### 2015-05-04 src/fiddler/peerdl.js
Add big file to test page

@@ -385,7 +385,7 @@ function DownloadManager(tracker, connectionManager, hashfn) {
   this.connectionManager = connectionManager;
   this.hashfn = hashfn;
   this.downloaded = {};
-  this.chunkSize = 1024; // 1KB chunk size
+  this.chunkSize = 25*1024; // chunk size in bytes
   // the following implementation detail will probably change in order to
   // improve performance, but the DownloadManager API should stay the same
   this.pending = {}; // map from hash to Downloads

### 2015-05-04 src/fiddler/peerdl.js
Fix bug
Do queueing properly.

@@ -210,12 +210,17 @@ ConnectionManager.prototype.send = function(peer, data) {
   } else if (dataChannel.readyState === 'connecting') {
     // queue data
     var old = dataChannel.onopen;
-    dataChannel.onopen = function(event) {
-      dataChannel.send(data);
-      if (typeof(old) !== 'undefined' && old !== null) {
-        old(event);
-      }
-    };
+    if (typeof(old) !== 'undefined' && old !== null) {
+      old.queued.push(data);
+    } else {
+      var f = {queued: [data]};
+      f.call = function(event) {
+        for (var i = 0; i < this.queued.length; i++) {
+          dataChannel.send(this.queued[i]);
+        }
+      };
+      dataChannel.onopen = f;
+    }
   }
 };
 
@@ -385,7 +390,7 @@ function DownloadManager(tracker, connectionManager, hashfn) {
   this.connectionManager = connectionManager;
   this.hashfn = hashfn;
   this.downloaded = {};
-  this.chunkSize = 25*1024; // chunk size in bytes
+  this.chunkSize = 10 * 1024; // chunk size in bytes
   // the following implementation detail will probably change in order to
   // improve performance, but the DownloadManager API should stay the same
   this.pending = {}; // map from hash to Downloads

### 2015-05-04 src/fiddler/zauberflote.js
Change tracker

@@ -3,7 +3,7 @@
  * Setup
  */
 
-var skt = io('http://localhost:5000');
+var skt = io('http://i.anish.io:5000');
 var tr = new Tracker(skt);
 var sc = new SignalingChannel(skt);
 var cm = new ConnectionManager(sc);

### 2015-05-05 doc/paper/paper.tex
Add paper template
added paper skeleton
Fix usepackage deps
added html5 localstorage to future work
assigning sections
adjusting assignments
Add diagram

--- 2015-03-31 doc/proposal/paper.tex
@@
 
-\usepackage{style, verbatim, url}
+\usepackage{style, verbatim, url, graphicx}
 \usepackage[colorlinks=true, citecolor=blue]{hyperref}
-\usepackage{cleveref}
-\usepackage{breakurl}
+\usepackage{cleveref, breakurl}
 
@@
 
+\newcommand{\zbf}{Zauberfl\"{o}te}
+\newcommand{\projtitle}{\zbf: A Transparent Peer-to-Peer CDN}
+
 \begin{document}
 
-\title{\Large \bf A Transparent Peer-to-Peer CDN}
+\title{\Large \bf \projtitle}
 
@@
 \maketitle
-
 \thispagestyle{empty}
@@
 
-\section{Design}
+% TODO Ankush
 
-\section{Goals}
+\section{\zbf\ API}
+
+% TODO Ankush
+
+\section{Implementation}
+
+\begin{figure}
+    \begin{centering}
+        \includegraphics[width=.8\linewidth]{components.eps}
+        \caption{Relationship between different components of the \zbf
+        peer-to-peer download service.}
+        \label{fig:components}
+    \end{centering}
+\end{figure}
+
+\subsection{Connection manager}
+
+% Anish
+
+\subsection{Download manager}
+
+% Anish
+
+\subsubsection{Chunking}
+
+\zbf\ divides assets into chunks; chunks are individually requested and sent between peers.
+We use a standard chunk size of 10240 bytes in our implementation; preliminary tests showed this chunk size to be reasonable.
+When a client asks for a resource, the download manager for that client determines the number of chunks for that resource from the specified size.
+The download manager then evenly distributes requests for these chunks among the peers with the resource.
+
+\subsubsection{Hash validation}
+
+% Anish
+
+\subsubsection{Parallelization}
+
+% Anish
+
+\subsubsection{Fault tolerance}
+
+% Anish
+
+\subsection{Tracker interface}
+
+% Katie
+
+\subsection{Signaling channel}
+
+% Katie
+
+\subsection{DOM injection layer}
+
+% Ankush
+
+\section{Evaluation}
+
+% TODO
+
+\section{Future work}
+
+\subsection{Per-chunk hash validation}
+
+% Ankush
+
+\subsection{Hybrid downloads over HTTP and P2P}
+
+% Ankush
+
+\subsection{Variable request sizes}
+
+% Katie
+
+\subsection{Bandwidth detection and prioritization}
+
+% Katie
+
+\subsection{Support for HTML5 media}
+
+% Ankush
+
+\section{Conclusions}
+
+% TODO
 

### 2015-05-05 src/fiddler/peerdl.js
deleting duplicated code

@@ -315,9 +315,6 @@ Download.prototype.start = function() {
           // update chunk data
           chunk.peer = peer;
           var now = new Date();
-          // update chunk data
-          chunk.peer = peer;
-          var now = new Date();
           chunk.lastSent = now.getTime();
           chunk.numTries = chunk.numTries + 1;
         }

### 2015-05-05 doc/paper/paper.tex
deleting duplicated code
Write implementation section

@@
 \usepackage{style, verbatim, url, graphicx}
-\usepackage[colorlinks=true, citecolor=blue]{hyperref}
+\usepackage[colorlinks=true, citecolor=blue, linkcolor=blue]{hyperref}
+\usepackage{caption}
 \usepackage{cleveref, breakurl}
@@
 \newcommand{\projtitle}{\zbf: A Transparent Peer-to-Peer CDN}
+\newcommand{\inclfigure}[3]{
+    \begin{figure}
+        \begin{centering}
+            \includegraphics[width=.8\linewidth]{#2}
+            \caption{#3}
+            \label{#1}
+        \end{centering}
+    \end{figure}
+}
 
@@
 
-\begin{figure}
-    \begin{centering}
-        \includegraphics[width=.8\linewidth]{components.eps}
-        \caption{Relationship between different components of the \zbf
-        peer-to-peer download service.}
-        \label{fig:components}
-    \end{centering}
-\end{figure}
+The \zbf\ architecture consists of several loosely-connected components (see
+figure~\ref{fig:components}). At the highest level, there is a download manager that
+provides a reliable download service. It relies on the tracker interface and
+the connection manager. The tracker interface facilitates communication with
+the central tracker for information about peers and file sizes, and the
+connection manager provides an interface for peer-to-peer message transfer.
+
+Our components rely on two standard APIs provided by modern browsers,
+WebSockets~\cite{w3c:websocket} for client-server communication and
+WebRTC~\cite{w3c:webrtc} for peer-to-peer communication.
+
+\inclfigure{fig:components}{components.eps}{
+    Relationship between different components of the \zbf\ peer-to-peer
+    download service. Components in gray are standard browser APIs.
+}
 

### 2015-05-05 doc/paper/paper.tex
chunking and tracker interface

--- 2015-05-05 doc/paper/paper.tex
@@
 
-\usepackage{style, verbatim, url, graphicx}
+\usepackage{style, verbatim, url}
 \usepackage[colorlinks=true, citecolor=blue]{hyperref}
@@
 
-\begin{figure}
-    \begin{centering}
-        \includegraphics[width=.8\linewidth]{components.eps}
-        \caption{Relationship between different components of the \zbf
-        peer-to-peer download service.}
-        \label{fig:components}
-    \end{centering}
-\end{figure}
+% Anish
 
@@
 The download manager then evenly distributes requests for these chunks among the peers with the resource.
+\\
+Requests for chunks time out on a per-chunk basis.
+We track the time \zbf\ last sent a request for each chunk; if this time exceeds a cutoff, we randomly choose another peer with the resource and send the chunk request to that peer.
+We periodically retrieve an updated peers list for this resource from the tracker.
 
@@
 
-% Katie
+The tracker is hosted on a remote server and tracks client connections.
+The download manager opens a websocket connection with the remote tracker, which registers the existence of this client.
+Via this socket, the download manager sends requests for data, specifying a desired resource via that resource's unique SHA1 hash.
+Upon disconnection, the tracker "forgets" about the client and erases all data about the client's held resources.
 
@@
 
-% TODO
+% Katie
 

### 2015-05-05 doc/paper/paper.tex
tracker section

@@
 The tracker is hosted on a remote server and tracks client connections.
-The download manager opens a websocket connection with the remote tracker, which registers the existence of this client.
-Via this socket, the download manager sends requests for data, specifying a desired resource via that resource's unique SHA1 hash.
-Upon disconnection, the tracker "forgets" about the client and erases all data about the client's held resources.
+The download manager opens a WebSocket connection with the remote tracker, which registers the existence of this client.
+Via this socket, the download manager can request a list of peers that have a certain resource, specifying the desired resource via that resource's unique SHA1 hash.
+After a client receives the full resource, the download manager publicizes that this client has the resource to the tracker.
+This client will then be included in the list of peers with that resource, as long as its WebSocket connection remains open.
+Upon WebSocket disconnection, the tracker "forgets" about the client and erases all data about the client's held resources.
 

### 2015-05-05 doc/paper/paper.tex
Add connection manager section

@@
 \inclfigure{fig:components}{components.eps}{
-    Relationship between different components of the \zbf\ peer-to-peer
-    download service. Components in gray are standard browser APIs.
+    Relationship between different client-side components of the \zbf\
+    peer-to-peer download service. Components in gray are standard browser
+    APIs.
 }
@@
 
-% Anish
+The connection manager is responsible for establishing connections between
+peers and facilitating peer-to-peer message transfers. It is a thin layer on
+top of WebRTC that handles maintaining connections with multiple peers,
+associating peers with peer IDs that are assigned by our tracker. It manages
+all signaling through the signaling channel, which implements signaling through
+our central server using WebSockets. At this time, this signaling server is the
+same server that is running the tracker, but they are logically separate
+components, so theoretically, they could be decoupled if needed for better load
+balancing.
 

### 2015-05-05 doc/paper/paper.tex
Add download manager

@@
 
-% Anish
+The download manager is the top-level client interface for peer-to-peer
+downloads. It provides an API where the client can provide a hash, and
+optionally, a fallback HTTP URL, and the download manager will asynchronously
+download the content associated with the hash and call a user-provided callback
+function when finished. The download manager implements reliable download,
+preferring peer-to-peer over HTTP when possible.
 

### 2015-05-05 doc/paper/paper.tex
server side tracker

--- 2015-05-05 doc/paper/paper.tex
@@
 
-The tracker is hosted on a remote server and tracks client connections.
-The download manager opens a WebSocket connection with the remote tracker, which registers the existence of this client.
-Via this socket, the download manager can request a list of peers that have a certain resource, specifying the desired resource via that resource's unique SHA1 hash.
-After a client receives the full resource, the download manager publicizes that this client has the resource to the tracker.
-This client will then be included in the list of peers with that resource, as long as its WebSocket connection remains open.
-Upon WebSocket disconnection, the tracker "forgets" about the client and erases all data about the client's held resources.
+Via the tracker interface, the download manager can request a list of peers that 
+have a certain resource, specifying the desired resource via that resource's 
+unique SHA1 hash. After a client receives the full resource, the download 
+manager publicizes that this client has the resource via this tracker interface,
+letting the central tracker know that it possesses the resource.
 
@@
 
-% Katie
+The signa
 
@@
 % Ankush
+
+\section{Server implementation}
+
+\subsection{Tracker}
+The tracker is hosted on a remote server and tracks client connections. 
+The client-side tracker interface  opens a WebSocket connection with the remote tracker, 
+which registers the existence of this client. The remote tracker responds to
+requests from the client for lists of peers with a given resource. When a client
+publicizes that it has a resource through the tracker interface, the remote tracker updates
+the list of peers with the resource to include this client, as 
+long as its WebSocket connection remains open. Upon WebSocket disconnection, 
+the tracker "forgets" about the client and erases all data about the client's 
+held resources.
+
+\subsection{WebRTC handshake channel}
 

### 2015-05-05 doc/paper/paper.tex
Add download manager related sections

@@
 
-% Anish
+When fetching content peer-to-peer, it is necessary to authenticate data that
+is downloaded. \zbf\ achieves this by using a cryptographic hash function to
+authenticate data that is downloaded. Assets that are to be downloaded
+peer-to-peer are identified by their hash, and once the download manager
+finishes downloading the content from peers, it verifies that the hash of the
+contents matches what is expected. The download manager rejects content if
+there is an authentication error. In the current implementation, if this
+occurs, the download manager falls back to downloading the content over HTTP
+from the fallback URL.
 
@@
 
-% Anish
+\zbf\ divides assets into chunks primarily to enable parallelization. Because
+individual peers may not have high outbound bandwidth, it is beneficial to
+download in parallel from many peers. Our implementation parallelizes chunk
+downloads, with pending chunk requests balanced between available peers in the
+network. If certain peers are slow to respond, the download manager
+automatically requests chunks from faster peers to optimize download time.
+Parallel downloads help reduce download latency.
 
@@
 
-% Anish
+Our download manager implements reliable download semantics. The implementation
+is resilient to peer failure, automatically re-requesting chunks from live
+peers when necessary. In the worst case, even if all peers go down, the
+implementation falls back to downloading over pure HTTP from the centralized
+server as a last resort. In any case, the download manager guarantees that the
+data will be downloaded and that the download will be authenticated.
 

### 2015-05-05 doc/paper/paper.tex
Fix syntax
server implementation

--- 2015-05-05 doc/paper/paper.tex
@@
 
-\zbf\ divides assets into chunks; chunks are individually requested and sent between peers.
-We use a standard chunk size of 10240 bytes in our implementation; preliminary tests showed this chunk size to be reasonable.
-When a client asks for a resource, the download manager for that client determines the number of chunks for that resource from the specified size.
-The download manager then evenly distributes requests for these chunks among the peers with the resource.
-\\
-Requests for chunks time out on a per-chunk basis.
-We track the time \zbf\ last sent a request for each chunk; if this time exceeds a cutoff, we randomly choose another peer with the resource and send the chunk request to that peer.
-We periodically retrieve an updated peers list for this resource from the tracker.
+\zbf\ divides assets into chunks; chunks are individually requested and
+sent between peers. We use a standard chunk size of 10240 bytes in our
+implementation; preliminary tests showed this chunk size to be reasonable.
+When a client asks for a resource, the download manager for that client
+determines the number of chunks for that resource from the specified size.
+The download manager then evenly distributes requests for these chunks
+among the peers with the resource. \\
+Requests for chunks time out on a per-chunk basis. We track the time \zbf\
+last sent a request for each chunk; if this time exceeds a cutoff, we randomly
+choose another peer with the resource and send the chunk request to that
+peer. We periodically retrieve an updated peers list for this resource
+from the tracker.
 
@@
 
+There are two main server-side components to \zbf\. First is the tracker,
+which maintains a mapping from resource hashes to the peers that have that
+resource. Second is the WebRTC handshake channel, which passes information
+between peers to enable them to open WebRTC data channels.
+
 \subsection{Tracker}
@@
 \subsection{WebRTC handshake channel}
+
+WebRTC handshake information--the offers, ICE candidates, and answers--are
+sent through the client-side signaling channel through a websocket to
+the server. The client-side signaling channel specifies a peer to which
+this WebRTC handshake information should be sent; if the server has an open
+websocket connection with that peer, the server passes that message to the peer.
 

### 2015-05-05 doc/paper/paper.tex

--- 2015-05-05 doc/paper/paper.tex
@@
 long as its WebSocket connection remains open. Upon WebSocket disconnection,
-the tracker "forgets" about the client and erases all data about the client's 
+the tracker ``forgets'' about the client and erases all data about the client's
 held resources.

### 2015-05-05 doc/paper/paper.tex
some future work sections

@@
 
-The signa
+The signaling channel enables
+% katie
 
@@
 
-% Katie
+Implementing variation in requested chunk sizes could allow \zbf\ to independently
+determine a more optimal chunk size for each asset. For instance, we hypothesize
+that different chunk sizes are optimal for differently sized assets, and potentially
+for different media types. If \zbf\ more intelligently determined the optimal size
+of chunks for each resource, overall download latency would decrease.
 
@@
 
-% Katie
+If \zbf\ could detect which peers have higher bandwidth connections, and thus
+are more capable of swiftly delivering data to a client, \zbf\ could prioritize
+requesting data from these peers. Perhaps \zbf\ could request larger chunks from
+peers with higher bandwidth connections. \zbf\ could also dynamically react to
+poor connections with peers during the chunk requesting process; chunk requests
+that subsequently time out could be redistributed more intelligently among
+peers with higher bandwidth connections.
 

### 2015-05-06 doc/paper/paper.tex
Fix bug
added signaling channel description

@@
 
-\inclfigure{fig:components}{components.eps}{
+\inclfigure{fig:components}{components.pdf}{
     Relationship between different client-side components of the \zbf\
@@
 
-The signaling channel enables
-% katie
+The signaling channel facilitates opening the WebRTC data channel connection between
+peers. The WebRTC protocol requires one peer to send a WebRTC offer and ICE candidate
+to the other peer, and that other peer to send back a WebRTC answer, for a peer-to-peer
+data channel to be opened. The server-side signaling channel facilitates this
+information transfer between peers by  directing offers, ICE candidates, and answers
+to their specified peer recipient.
 

### 2015-05-06 doc/paper/paper.tex
work on paper

@@
 \begin{abstract}
-
+% TODO
 \end{abstract}
@@
 \section{Introduction}
+In today's day and age, it's very common for personal blogs and other small websites to gain popularity on websites such as Reddit.
+Since these websites usually experience much smaller loads, the hardware devoted to hosting them is typically not powerful enough to cope with a large amount of traffic.
+These sudden, unexpected bursts of traffic often result in websites loading at extremely slow speeds (or not loading at all) and is colloquially known as the "Reddit Hug of Death".
 
-% TODO Ankush
+Typical means for dealing with this situation involve utilizing Content Delivery Networks (CDNs), but these are usually out of the budgetary constraints for websites which only experience such loads on an occasional basis.
+
+Currently, peer-to-peer content delivery networks do exist, yet are usually
+closed-source. PeerCDN~\cite{peercdn} is one such example found in
+industry; it offloads site hosting to users of a site, significantly lowering strain on content delivery from a central source. \zbf\ is an open-sourced system
+that will allow developers to easily integrate a peer-to-peer CDN to expedite
+content delivery to clients even when operating under heavy load.
+
+\zbf's design is based on the BitTorrent protocol~\cite{cohen:bittorrent}, where
+clients requesting content will attempt to receive chunks of data from other
+clients, rather than retrieving the entire file from a central server.
 
@@
 
-% TODO Ankush
+\zbf\ supports peer-to-peer loading for CSS (via \texttt{link} elements), Javascript (via \texttt{script} elements), and images (via \texttt{img} elements).
+In order for an existing website to utilize \zbf, the developer simply needs to make two changes to the DOM elements.
+
+The first change that must be made is renaming the \texttt{src} or \texttt{href} attribute to  \texttt{data-zf-fallback}.
+\zbf\ uses the \texttt{data-zf-fallback} attribute in order to (1) prevent the browser from automatically fetching the resources, and (2) provide a URL to be used in the event that the peer-to-peer network is unable to serve the content.
+
+The second attribute that must be present on a DOM element that is fetched by \zbf\ is the \texttt{data-zf-hash} attribute.
+The \texttt{data-zf-hash} attribute is the SHA1 hash of that resource, which can be computed by the developer, and is utilized by \zbf\ in order to ensure integrity of data fetched via peer-to-peer interaction.
 
@@
 \subsection{DOM injection layer}
-
-% Ankush
+%! Ankush
 
@@
 \subsection{Per-chunk hash validation}
+As of right now, \zbf\ verifies the integrity of the downloaded resource once all chunks have been retrieved and joined.
+In normal circumstances where all chunks successfully download, this may not prove to be an issue.
+However, waiting until all chunks are downloaded and combined to verify the file means that if a single chunk had been corrupted or compromised, all chunks for the file would need to be downloaded, combined, and verified again.
 
-% Ankush
+An improvement to \zbf\ that would mitigate this issue would be to have the Tracker module provide checksums for each chunk.
+From the user's perspective, the \texttt{data-zf-hash} attribute currently used to store the hash of the file would be replaced with the hash of the JSON object storing a list of the hashes for each chunk.
+Upon connection to the tracker, each client would receive that list and verify its integrity, and then be able to verify and redownload each chunk independently in the event of failure..
 
@@
 
-% Ankush
+Another improvement to \zbf\ would be to allow it to parallelize downloads via HTTP and P2P transfers simultaneously.
+By using the \texttt{Range} HTTP header attribute, \zbf\ could fetch the same data as contained in P2P chunks from the HTTP fallback server.
+By utilizing both HTTP and P2P, \zbf\ may be able to provide service speed that is expected in all instances to be faster than simply using HTTP alone.
 
@@
 \subsection{Support for HTML5 media}
+It is possible to add functionality such that \zbf\ can construct \texttt{ReadableStream}s (as specified by the Streams standard) %TODO: cite https://streams.spec.whatwg.org
+from the chunks of data as it receives them.
+Using this stream, the DOM injection layer could feasibly replace HTML5 media elements such as embedded Video and Audio.
+Since these types of media are particularly large in size, being able to distribute them in a decentralized, peer-to-peer manner could provide substantial load reduction for the central server.
 
-% Ankush
+\subsection{Automatic conversion to \zbf }
+% TODO
 

### 2015-05-07 doc/paper/paper.tex
Fix command spacing

@@
 
-\usepackage{style, verbatim, url, graphicx}
+\usepackage{style, verbatim, url, graphicx, xspace}
 \usepackage[colorlinks=true, citecolor=blue, linkcolor=blue]{hyperref}
@@
 
-\newcommand{\zbf}{Zauberfl\"{o}te}
+\newcommand{\zbf}{Zauberfl\"{o}te\xspace}
 \newcommand{\projtitle}{\zbf: A Transparent Peer-to-Peer CDN}
@@
 closed-source. PeerCDN~\cite{peercdn} is one such example found in
-industry; it offloads site hosting to users of a site, significantly lowering strain on content delivery from a central source. \zbf\ is an open-sourced system
+industry; it offloads site hosting to users of a site, significantly lowering strain on content delivery from a central source. \zbf is an open-sourced system
 that will allow developers to easily integrate a peer-to-peer CDN to expedite
@@
 
-\section{\zbf\ API}
+\section{\zbf API}
 
-\zbf\ supports peer-to-peer loading for CSS (via \texttt{link} elements), Javascript (via \texttt{script} elements), and images (via \texttt{img} elements).
+\zbf supports peer-to-peer loading for CSS (via \texttt{link} elements), Javascript (via \texttt{script} elements), and images (via \texttt{img} elements).
 In order for an existing website to utilize \zbf, the developer simply needs to make two changes to the DOM elements.
@@
 The first change that must be made is renaming the \texttt{src} or \texttt{href} attribute to  \texttt{data-zf-fallback}.
-\zbf\ uses the \texttt{data-zf-fallback} attribute in order to (1) prevent the browser from automatically fetching the resources, and (2) provide a URL to be used in the event that the peer-to-peer network is unable to serve the content.
+\zbf uses the \texttt{data-zf-fallback} attribute in order to (1) prevent the browser from automatically fetching the resources, and (2) provide a URL to be used in the event that the peer-to-peer network is unable to serve the content.
 
-The second attribute that must be present on a DOM element that is fetched by \zbf\ is the \texttt{data-zf-hash} attribute.
-The \texttt{data-zf-hash} attribute is the SHA1 hash of that resource, which can be computed by the developer, and is utilized by \zbf\ in order to ensure integrity of data fetched via peer-to-peer interaction.
+The second attribute that must be present on a DOM element that is fetched by \zbf is the \texttt{data-zf-hash} attribute.
+The \texttt{data-zf-hash} attribute is the SHA1 hash of that resource, which can be computed by the developer, and is utilized by \zbf in order to ensure integrity of data fetched via peer-to-peer interaction.
 
@@
 
-The \zbf\ architecture consists of several loosely-connected components (see
+The \zbf architecture consists of several loosely-connected components (see
 figure~\ref{fig:components}). At the highest level, there is a download manager that
@@
 \inclfigure{fig:components}{components.pdf}{
-    Relationship between different client-side components of the \zbf\
+    Relationship between different client-side components of the \zbf
     peer-to-peer download service. Components in gray are standard browser
@@
 
-\zbf\ divides assets into chunks; chunks are individually requested and
+\zbf divides assets into chunks; chunks are individually requested and
 sent between peers. We use a standard chunk size of 10240 bytes in our
@@
 among the peers with the resource. \\
-Requests for chunks time out on a per-chunk basis. We track the time \zbf\
+Requests for chunks time out on a per-chunk basis. We track the time \zbf
 last sent a request for each chunk; if this time exceeds a cutoff, we randomly
@@
 When fetching content peer-to-peer, it is necessary to authenticate data that
-is downloaded. \zbf\ achieves this by using a cryptographic hash function to
+is downloaded. \zbf achieves this by using a cryptographic hash function to
 authenticate data that is downloaded. Assets that are to be downloaded
@@
 
-\zbf\ divides assets into chunks primarily to enable parallelization. Because
+\zbf divides assets into chunks primarily to enable parallelization. Because
 individual peers may not have high outbound bandwidth, it is beneficial to
@@
 
-There are two main server-side components to \zbf\. First is the tracker,
+There are two main server-side components to \zbf. First is the tracker,
 which maintains a mapping from resource hashes to the peers that have that
@@
 \subsection{Per-chunk hash validation}
-As of right now, \zbf\ verifies the integrity of the downloaded resource once all chunks have been retrieved and joined.
+As of right now, \zbf verifies the integrity of the downloaded resource once all chunks have been retrieved and joined.
 In normal circumstances where all chunks successfully download, this may not prove to be an issue.
@@
 
-An improvement to \zbf\ that would mitigate this issue would be to have the Tracker module provide checksums for each chunk.
+An improvement to \zbf that would mitigate this issue would be to have the Tracker module provide checksums for each chunk.
 From the user's perspective, the \texttt{data-zf-hash} attribute currently used to store the hash of the file would be replaced with the hash of the JSON object storing a list of the hashes for each chunk.
@@
 
-Another improvement to \zbf\ would be to allow it to parallelize downloads via HTTP and P2P transfers simultaneously.
-By using the \texttt{Range} HTTP header attribute, \zbf\ could fetch the same data as contained in P2P chunks from the HTTP fallback server.
-By utilizing both HTTP and P2P, \zbf\ may be able to provide service speed that is expected in all instances to be faster than simply using HTTP alone.
+Another improvement to \zbf would be to allow it to parallelize downloads via HTTP and P2P transfers simultaneously.
+By using the \texttt{Range} HTTP header attribute, \zbf could fetch the same data as contained in P2P chunks from the HTTP fallback server.
+By utilizing both HTTP and P2P, \zbf may be able to provide service speed that is expected in all instances to be faster than simply using HTTP alone.
 
@@
 
-Implementing variation in requested chunk sizes could allow \zbf\ to independently
+Implementing variation in requested chunk sizes could allow \zbf to independently
 determine a more optimal chunk size for each asset. For instance, we hypothesize
 that different chunk sizes are optimal for differently sized assets, and potentially
-for different media types. If \zbf\ more intelligently determined the optimal size
+for different media types. If \zbf more intelligently determined the optimal size
 of chunks for each resource, overall download latency would decrease.
@@
 
-If \zbf\ could detect which peers have higher bandwidth connections, and thus
-are more capable of swiftly delivering data to a client, \zbf\ could prioritize
-requesting data from these peers. Perhaps \zbf\ could request larger chunks from
-peers with higher bandwidth connections. \zbf\ could also dynamically react to
+If \zbf could detect which peers have higher bandwidth connections, and thus
+are more capable of swiftly delivering data to a client, \zbf could prioritize
+requesting data from these peers. Perhaps \zbf could request larger chunks from
+peers with higher bandwidth connections. \zbf could also dynamically react to
 poor connections with peers during the chunk requesting process; chunk requests
@@
 \subsection{Support for HTML5 media}
-It is possible to add functionality such that \zbf\ can construct \texttt{ReadableStream}s (as specified by the Streams standard) %TODO: cite https://streams.spec.whatwg.org
+It is possible to add functionality such that \zbf can construct \texttt{ReadableStream}s (as specified by the Streams standard) %TODO: cite https://streams.spec.whatwg.org
 from the chunks of data as it receives them.
@@
 
-\subsection{Automatic conversion to \zbf }
+\subsection{Automatic conversion to \zbf}
 % TODO

### 2015-05-07 src/fiddler/peerdl.js
Implement exponential backoff

@@ -332,7 +332,9 @@ Download.prototype.start = function() {
 }
 
 Download.prototype.timedOut = function(lastSent, numTries) {
-  var timeoutCutoff = 100; // 100 ms
+  var base = 100; // ms
+  var ceiling = 2000; // ms
+  var timeout = Math.min(base * Math.pow(2, numTries), ceiling); // ms
   var now = new Date();
   if (lastSent == null || now.getTime() - lastSent > timeoutCutoff) {
     return true;

### 2015-05-07 src/fiddler/peerdl.js
Fix

@@ -336,7 +336,7 @@ Download.prototype.timedOut = function(lastSent, numTries) {
   var ceiling = 2000; // ms
   var timeout = Math.min(base * Math.pow(2, numTries), ceiling); // ms
   var now = new Date();
-  if (lastSent == null || now.getTime() - lastSent > timeoutCutoff) {
+  if (lastSent == null || now.getTime() - lastSent > timeout) {
     return true;
   }
   return false;

### 2015-05-07 doc/paper/paper.tex
Add todos
still needs dom injection, evaluation, and conclusion parts of paper

@@
 \begin{abstract}
-% TODO
+\zbf is a peer-to-peer system based on the BitTorrent protocol that uses WebRTC
+to distribute content between peers. \zbf provides an easily accessible way for
+developers to alleviate content delivery bandwidth concerns by marking DOM elements
+such that \zbf will fetch these resources from peers with that resource. The \zbf
+system has server-side tracker and WebRTC signaling channel components, as well
+as client-side scripting that requests and delivers content between peers.
+This version of the system implements basic chunking, parallelism, and fault tolerance.
+In this paper, we describe the motivation for \zbf and the design and implementation of the
+different components that comprise the system. We then detail future improvements
+that could be made to increase the robustness and performance of the overall system.
 \end{abstract}
@@
 \section{Introduction}
-In today's day and age, it's very common for personal blogs and other small websites to gain popularity on websites such as Reddit.
-Since these websites usually experience much smaller loads, the hardware devoted to hosting them is typically not powerful enough to cope with a large amount of traffic.
-These sudden, unexpected bursts of traffic often result in websites loading at extremely slow speeds (or not loading at all) and is colloquially known as the "Reddit Hug of Death".
+It is common for personal blogs and other small websites to gain sudden attention
+on large, high-traffic websites such as Reddit. Since these websites usually
+experience much smaller traffic loads, the hardware devoted to hosting them
+is typically not powerful enough to cope with this large influx of content requests.
+These sudden, unexpected bursts of traffic often result in websites loading at
+extremely slow speeds, or not loading at all, and is colloquially known as the
+"Reddit Hug of Death". \\
 
-Typical means for dealing with this situation involve utilizing Content Delivery Networks (CDNs), but these are usually out of the budgetary constraints for websites which only experience such loads on an occasional basis.
+Typical means for dealing with this situation involve utilizing Content Delivery
+Networks (CDNs), but these are usually out of the budgetary constraints for
+websites which only experience such loads on an occasional basis. An ideal
+solution would be a lightweight means to mimic the benefits of an ordinary
+CDN, which is typically backed by a robust network of machines. \\
 
-Currently, peer-to-peer content delivery networks do exist, yet are usually
-closed-source. PeerCDN~\cite{peercdn} is one such example found in
-industry; it offloads site hosting to users of a site, significantly lowering strain on content delivery from a central source. \zbf is an open-sourced system
-that will allow developers to easily integrate a peer-to-peer CDN to expedite
-content delivery to clients even when operating under heavy load.
+In this paper, we present \zbf, a peer-to-peer CDN. \zbf provides an easy way
+for developers to distribute content to clients via a peer-to-peer network,
+rather than directly from the central server that hosts the content. \zbf
+is comprised of a server-side component and a client-side component. The
+centralized, server-side component both tracks resource propagation metadata
+and acts as an assist for opening peer-to-peer data channel connections. The
+lightweight client-side component requests resources from peers and distributes
+resources in response to peer requests. \\
 
-\zbf's design is based on the BitTorrent protocol~\cite{cohen:bittorrent}, where
-clients requesting content will attempt to receive chunks of data from other
-clients, rather than retrieving the entire file from a central server.
+\zbf's design is based on the BitTorrent protocol~\cite{cohen:bittorrent}, by which
+clients requesting content attempt to receive chunks of data from other
+clients, rather than retrieving the entire file from a central server. As
+with BitTorrent trackers, any developer could host their own tracker and service
+it to connect peers requesting a resource with peers distributing the resource. \\
+
+The \zbf client-side code runs purely in the browser, and is completely transparent
+to the user. The user does not have to install any application on their
+computer to obtain desired resources peer-to-peer. As a result, the \zbf client
+code only runs when a user is currently visiting the website, therefore adding
+no burden to the user from constant background processes. \\
+
+In designing \zbf, we took into consideration the unique problems presented
+by browser-to-browser content streaming. Website visitor churn is often very
+high with any type of website; our system had to be robust under these common
+conditions. \zbf forms peer-to-peer connections quickly and immediately streams
+requested resources through these data channel connections. \zbf also recovers
+quickly from data request failures; the \zbf data chunking component minimizes
+latency from these failures and quickly retries resource requests with other
+peers.
 
@@
 
-\zbf supports peer-to-peer loading for CSS (via \texttt{link} elements), Javascript (via \texttt{script} elements), and images (via \texttt{img} elements).
-In order for an existing website to utilize \zbf, the developer simply needs to make two changes to the DOM elements.
+\zbf supports peer-to-peer loading for CSS (via \texttt{link} elements),
+Javascript (via \texttt{script} elements), and images (via \texttt{img} elements).
+For an existing website to utilize \zbf, the developer simply needs
+to make two changes to the DOM elements. \\
 
-The first change that must be made is renaming the \texttt{src} or \texttt{href} attribute to  \texttt{data-zf-fallback}.
-\zbf uses the \texttt{data-zf-fallback} attribute in order to (1) prevent the browser from automatically fetching the resources, and (2) provide a URL to be used in the event that the peer-to-peer network is unable to serve the content.
+The first change is renaming the \texttt{src} or \texttt{href} attribute to
+\texttt{data-zf-fallback}. \zbf uses the \texttt{data-zf-fallback} attribute
+in order to (1) prevent the browser from automatically fetching the resources,
+and (2) provide a URL to be used in the event that the peer-to-peer network
+is unable to serve the content. \\
 
-The second attribute that must be present on a DOM element that is fetched by \zbf is the \texttt{data-zf-hash} attribute.
-The \texttt{data-zf-hash} attribute is the SHA1 hash of that resource, which can be computed by the developer, and is utilized by \zbf in order to ensure integrity of data fetched via peer-to-peer interaction.
+The second attribute that must be present on a DOM element that is fetched by
+\zbf is the \texttt{data-zf-hash} attribute. The \texttt{data-zf-hash} attribute
+is the SHA1 hash of that resource, which can be computed by the developer, and
+is utilized by \zbf to ensure integrity of data fetched via peer-to-peer interaction.
 
@@
 the central tracker for information about peers and file sizes, and the
-connection manager provides an interface for peer-to-peer message transfer.
+connection manager provides an interface for peer-to-peer message transfer. \\
 
@@
 same server that is running the tracker, but they are logically separate
-components, so theoretically, they could be decoupled if needed for better load
+components, so theoretically, they could be decoupled if the need arises for better load
 balancing.
@@
 The download manager is the top-level client interface for peer-to-peer
-downloads. It provides an API where the client can provide a hash, and
-optionally, a fallback HTTP URL, and the download manager will asynchronously
+downloads. It provides an API by which the client can provide a hash, and
+optionally, a fallback HTTP URL. The download manager will asynchronously
 download the content associated with the hash and call a user-provided callback
@@
 When a client asks for a resource, the download manager for that client
-determines the number of chunks for that resource from the specified size.
+determines the number of chunks for that resource from the resource's total size.
 The download manager then evenly distributes requests for these chunks
@@
 peer. We periodically retrieve an updated peers list for this resource
-from the tracker.
+from the tracker. \zbf uses exponential backoff when sending chunk requests
+so we don't flood peers with requests as a result of slow network connectivity.
 
@@
 \subsection{DOM injection layer}
-%! Ankush
+% Ankush
 
@@
 \subsection{Per-chunk hash validation}
-As of right now, \zbf verifies the integrity of the downloaded resource once all chunks have been retrieved and joined.
-In normal circumstances where all chunks successfully download, this may not prove to be an issue.
-However, waiting until all chunks are downloaded and combined to verify the file means that if a single chunk had been corrupted or compromised, all chunks for the file would need to be downloaded, combined, and verified again.
+As of right now, \zbf verifies the integrity of the downloaded resource once all
+chunks have been retrieved and joined. In normal circumstances where all chunks
+successfully download, this may not prove to be an issue. However, waiting until
+all chunks are downloaded and combined to verify the file means that if a single
+chunk had been corrupted or compromised, all chunks for the file would need to be
+downloaded, combined, and verified again. \\
 
-An improvement to \zbf that would mitigate this issue would be to have the Tracker module provide checksums for each chunk.
-From the user's perspective, the \texttt{data-zf-hash} attribute currently used to store the hash of the file would be replaced with the hash of the JSON object storing a list of the hashes for each chunk.
-Upon connection to the tracker, each client would receive that list and verify its integrity, and then be able to verify and redownload each chunk independently in the event of failure..
+An improvement to \zbf that would mitigate this issue would be to have the Tracker
+module provide checksums for each chunk. From the user's perspective, the
+\texttt{data-zf-hash} attribute currently used to store the hash of the file
+would be replaced with the hash of the JSON object storing a list of the hashes
+for each chunk. Upon connection to the tracker, each client would receive that
+list and verify its integrity, and then be able to verify and redownload each chunk
+independently in the event of failure.
 
@@
 \subsection{Support for HTML5 media}
-It is possible to add functionality such that \zbf can construct \texttt{ReadableStream}s (as specified by the Streams standard) %TODO: cite https://streams.spec.whatwg.org
-from the chunks of data as it receives them.
-Using this stream, the DOM injection layer could feasibly replace HTML5 media elements such as embedded Video and Audio.
-Since these types of media are particularly large in size, being able to distribute them in a decentralized, peer-to-peer manner could provide substantial load reduction for the central server.
+It is possible to add functionality such that \zbf can construct
+\texttt{ReadableStream}s (as specified by the Streams standard)
+%TODO: cite https://streams.spec.whatwg.org
+from the chunks of data as it receives them. Using this stream, the DOM injection
+layer could feasibly replace HTML5 media elements such as embedded Video and Audio.
+Since these types of media are particularly large in size, being able to distribute
+them in a decentralized, peer-to-peer manner could provide substantial load
+reduction for the central server.
 
 \subsection{Automatic conversion to \zbf}
-% TODO
+Developers can integrate their sites to use \zbf by adding attribute tags to
+the site resources they wish to be distributed using the system. However, sites feature
+dozens of resources; as a result, adapting a site to use \zbf could present a
+burden on the developer. If we were to provide a script that developers could use
+to change HTML such that all resources were loaded using \zbf, this would ease
+integration pains.
+
+\section{Related work}
+
+% TODO cite peercdn in bibtex
+Currently, alternative peer-to-peer content delivery networks do exist. The three
+prominent peer-to-peer CDNs are PeerJS, PeerCDN, and Peer5. PeerJS is open-sourced
+and similarly transparent, but only encapsulates the functionality of our connection manager
+module. PeerCDN~\cite{peercdn} is a closed-source alternative providing  similar
+functionality to \zbf; it offloads site content delivery to users of a site,
+significantly lowering strain on the central source. However, PeerCDN was acquired by
+Yahoo! and no longer exists. Finally, Peer5 is a service used by companies today.
+Unfortunately, Peer5 is a paid service that is entirely closed-source; the Peer5 code is
+not transparent to the clients on which it runs.
 
@@
 % Katie
+\zbf is an open-sourced system
+that will allow developers to easily integrate a peer-to-peer CDN to expedite
+content delivery to clients even when operating under heavy load.
 

### 2015-05-07 src/fiddler/peerdl.js
Increase chunk size

@@ -389,7 +389,7 @@ function DownloadManager(tracker, connectionManager, hashfn) {
   this.connectionManager = connectionManager;
   this.hashfn = hashfn;
   this.downloaded = {};
-  this.chunkSize = 10 * 1024; // chunk size in bytes
+  this.chunkSize = 25 * 1024; // chunk size in bytes
   // the following implementation detail will probably change in order to
   // improve performance, but the DownloadManager API should stay the same
   this.pending = {}; // map from hash to Downloads

### 2015-05-07 eval/src/main/scala/Driver.scala
Add half-built driver

@@ -1,0 +1,40 @@
+import org.openqa.selenium._
+import org.openqa.selenium.remote._
+import java.net.URL
+import collection.JavaConversions._
+import java.util.concurrent.TimeUnit._
+
+object Driver {
+
+  def run(numWindows: Int) {
+    val capabilities = DesiredCapabilities.chrome()
+    val url = new URL("http://localhost:9515")
+    val driver = new RemoteWebDriver(url, capabilities)
+    val jse = driver.asInstanceOf[JavascriptExecutor]
+    for (i <- 1 to numWindows) {
+      jse.executeScript("window.open();");
+    }
+    var windows = driver.getWindowHandles()
+    def switchTo(window: String) {
+      driver.switchTo().window(window)
+    }
+    for (window <- windows) {
+      switchTo(window)
+      jse.executeAsyncScript("""
+        var callback = arguments[arguments.length - 1];
+        callback();
+        setTimeout(function() {
+          window.location = "http://localhost:8000/frontend.html";
+        }, 0);
+        """
+      )
+    }
+    // Thread.sleep(10000)
+    // driver.quit()
+  }
+
+  def main(args: Array[String]) {
+    run(10)
+  }
+
+}

### 2015-05-07 provision/setup.sh
Add Vagrantfile

@@ -1,0 +1,10 @@
+sudo apt-get update
+sudo apt-get install -y nginx
+patch /etc/nginx/sites-available/default <<EOF
+24c24
+< 	root /usr/share/nginx/html;
+---
+> 	root /www;
+36a37
+> 	add_header 'Access-Control-Allow-Origin' '*';
+EOF

### 2015-05-07 www/peerdl.js
Add demo

@@ -1,0 +1,1 @@
+../src/fiddler/peerdl.js

### 2015-05-07 www/socket.io.js

@@ -1,0 +1,1 @@
+../src/fiddler/socket.io.js

### 2015-05-07 www/zauberflote.js

@@ -1,0 +1,1 @@
+../src/fiddler/zauberflote.js

### 2015-05-07 provision/setup.sh
Fix

@@ -8,3 +8,4 @@ patch /etc/nginx/sites-available/default <<EOF
 36a37
 > 	add_header 'Access-Control-Allow-Origin' '*';
 EOF
+sudo service nginx restart

### 2015-05-07 eval/src/main/scala/Driver.scala
Update

@@ -24,7 +24,7 @@ object Driver {
         var callback = arguments[arguments.length - 1];
         callback();
         setTimeout(function() {
-          window.location = "http://localhost:8000/frontend.html";
+          window.location = "http://localhost:8080/benchmark.html";
         }, 0);
         """
       )

### 2015-05-07 eval/src/main/scala/Driver.scala
Add HTTP only mode

@@ -11,7 +11,7 @@ object Driver {
     val url = new URL("http://localhost:9515")
     val driver = new RemoteWebDriver(url, capabilities)
     val jse = driver.asInstanceOf[JavascriptExecutor]
-    for (i <- 1 to numWindows) {
+    for (i <- 1 until numWindows) {
       jse.executeScript("window.open();");
     }
     var windows = driver.getWindowHandles()
@@ -24,7 +24,8 @@ object Driver {
         var callback = arguments[arguments.length - 1];
         callback();
         setTimeout(function() {
-          window.location = "http://localhost:8080/benchmark.html";
+          window.location = "http://localhost:8080/benchmark.html?http_only";
+          // window.location = "http://localhost:8080/benchmark.html";
         }, 0);
         """
       )

### 2015-05-07 src/fiddler/peerdl.js

@@ -28,6 +28,11 @@ function Tracker(socket) {
 }
 
 Tracker.prototype.getInfo = function(hash, callback) {
+  if (this.HTTP_ONLY === true) {
+    callback({hash: hash, size: -1, peers: []});
+    return;
+  }
+
   var seq = ++this.counter;
   var req = {seq: seq, hash: hash};
   this.socket.emit('peer-request', JSON.stringify(req));
@@ -441,7 +446,8 @@ function xhrGet(url, callback) {
   // the server needs to send the Access-Control-Allow-Origin: *
   // header
   var xhr = new XMLHttpRequest();
-  xhr.open('GET', url, true);
+  // hack to avoid using cached data
+  xhr.open('GET', url + '?' + Math.random(), true);
   xhr.responseType = 'arraybuffer';
   xhr.onerror = function(e) {
     callback(null, e);

### 2015-05-07 src/fiddler/zauberflote.js

@@ -13,6 +13,10 @@ var dm = new DownloadManager(tr, cm, sha1.hash);
  * Automatic p2p download
  */
 
+if (window.location.toString().indexOf('http_only') !== -1) {
+  tr.HTTP_ONLY = true;
+}
+
 $(document).ready(function() {
   var p2pAssets = $('[data-zf-hash]');
   for (var i = 0; i < p2pAssets.length; i++) {

### 2015-05-07 eval/src/main/scala/Driver.scala
Add window to driver communication

@@ -3,6 +3,8 @@ import org.openqa.selenium.remote._
 import java.net.URL
 import collection.JavaConversions._
 import java.util.concurrent.TimeUnit._
+import com.corundumstudio.socketio._
+import com.corundumstudio.socketio.listener._
 
 object Driver {
 
@@ -30,12 +32,37 @@ object Driver {
         """
       )
     }
-    // Thread.sleep(10000)
-    // driver.quit()
+    def done(): Boolean = {
+      for (window <- windows) {
+        switchTo(window)
+        var res = jse.executeScript("""
+          return loadTime;
+          """
+        )
+        if (res == null || res.asInstanceOf[String] == "") {
+          return false
+        }
+      }
+      return true
+    }
+
+    while (!done()) {
+      Thread.sleep(250)
+    }
+
+    for (window <- windows) {
+      switchTo(window)
+      var res = jse.executeScript("""
+        return loadTime;
+        """
+      )
+      println(res.asInstanceOf[String])
+    }
+    driver.quit()
   }
 
   def main(args: Array[String]) {
-    run(10)
+    run(3)
   }
 
 }

### 2015-05-07 eval/src/main/scala/Driver.scala
Fix race condition

@@ -26,8 +26,8 @@ object Driver {
         var callback = arguments[arguments.length - 1];
         callback();
         setTimeout(function() {
-          window.location = "http://localhost:8080/benchmark.html?http_only";
-          // window.location = "http://localhost:8080/benchmark.html";
+          // window.location = "http://localhost:8080/benchmark.html?http_only";
+          window.location = "http://localhost:8080/benchmark.html";
         }, 0);
         """
       )
@@ -36,7 +36,7 @@ object Driver {
       for (window <- windows) {
         switchTo(window)
         var res = jse.executeScript("""
-          return loadTime;
+          return (window.loadTime || "");
           """
         )
         if (res == null || res.asInstanceOf[String] == "") {
@@ -62,7 +62,12 @@ object Driver {
   }
 
   def main(args: Array[String]) {
-    run(3)
+    var t = new Thread(new Runnable {
+      def run() { Driver.run(5) }
+    })
+    t.start()
+    run(5)
+    t.join()
   }
 
 }

### 2015-05-07 src/fiddler/zauberflote.js
Update tracker URL

@@ -3,7 +3,7 @@
  * Setup
  */
 
-var skt = io('http://i.anish.io:5000');
+var skt = io('http://localhost:5000');
 var tr = new Tracker(skt);
 var sc = new SignalingChannel(skt);
 var cm = new ConnectionManager(sc);

### 2015-05-07 eval/src/main/scala/Driver.scala
Fix

@@ -3,8 +3,6 @@ import org.openqa.selenium.remote._
 import java.net.URL
 import collection.JavaConversions._
 import java.util.concurrent.TimeUnit._
-import com.corundumstudio.socketio._
-import com.corundumstudio.socketio.listener._
 
 object Driver {
 
@@ -47,7 +45,7 @@ object Driver {
     }
 
     while (!done()) {
-      Thread.sleep(250)
+      Thread.sleep(1000)
     }
 
     for (window <- windows) {
@@ -58,16 +56,12 @@ object Driver {
       )
       println(res.asInstanceOf[String])
     }
-    driver.quit()
+    // driver.quit()
   }
 
   def main(args: Array[String]) {
-    var t = new Thread(new Runnable {
-      def run() { Driver.run(5) }
-    })
-    t.start()
     run(5)
-    t.join()
+    run(5)
   }
 
 }

### 2015-05-07 eval/src/main/scala/Driver.scala
Implement driver methods

@@ -6,62 +6,111 @@ import java.util.concurrent.TimeUnit._
 
 object Driver {
 
-  def run(numWindows: Int) {
-    val capabilities = DesiredCapabilities.chrome()
-    val url = new URL("http://localhost:9515")
-    val driver = new RemoteWebDriver(url, capabilities)
+  val WINDOWS_PER_DRIVER = 5
+  require(WINDOWS_PER_DRIVER > 0)
+
+  type Window = (RemoteWebDriver, String)
+
+  def switchTo(window: Window) {
+    window._1.switchTo().window(window._2)
+  }
+
+  def openWindow(driver: RemoteWebDriver) {
     val jse = driver.asInstanceOf[JavascriptExecutor]
-    for (i <- 1 until numWindows) {
-      jse.executeScript("window.open();");
+    jse.executeScript("window.open();")
+  }
+
+  def prepare(numWindows: Int): (Seq[(RemoteWebDriver, String)], Seq[RemoteWebDriver]) = {
+    val dc = DesiredCapabilities.chrome()
+    val url = new URL("http://localhost:9515")
+    val mod = numWindows % WINDOWS_PER_DRIVER
+    val numDrivers = numWindows / WINDOWS_PER_DRIVER + (if (mod != 0) 1 else 0)
+    val drivers = for (i <- 1 to numDrivers) yield {
+      new RemoteWebDriver(url, dc)
     }
-    var windows = driver.getWindowHandles()
-    def switchTo(window: String) {
-      driver.switchTo().window(window)
+    for {
+      (driver, i) <- drivers.zipWithIndex
+      toSpawn = if (i < drivers.length - 1 || mod == 0) WINDOWS_PER_DRIVER else mod
+      _ <- 1 until toSpawn
+    } {
+      openWindow(driver)
     }
-    for (window <- windows) {
-      switchTo(window)
-      jse.executeAsyncScript("""
-        var callback = arguments[arguments.length - 1];
-        callback();
-        setTimeout(function() {
-          // window.location = "http://localhost:8080/benchmark.html?http_only";
+    val windows = drivers flatMap { driver =>
+      driver.getWindowHandles() map { (driver, _) }
+    }
+    (windows, drivers)
+  }
+
+  def asyncLoadPage(window: Window, httpOnly: Boolean) {
+    switchTo(window)
+    val jse = window._1.asInstanceOf[JavascriptExecutor]
+    jse.executeAsyncScript(s"""
[…]

### 2015-05-07 doc/paper/paper.tex
adding results subsections
basic eval description

@@
 
-% TODO
+We tested \zbf on a simple site that loads one large 768KB image from a remote server.
+In our tests, we compare page load times using both plain HTTP and \zbf in a range of
+scenarios. Specifically, we varied two parameters: the number of seeding peers and the
+number of leeching peers. A seeding peer is a peer that has the desired resource, which
+in our tests, was the single image on the site. A leeching peer is a peer that desires the
+resource, so must request it either from the central site host or from peers with the resource.
+Our tests launched a certain number of seeding peers, then launched a number of
+leeching peers, measuring the average load latency for the leeching peers. We compare
+this latency data with the page load latency when the leeching peers must load the content from the
+central site host.
+
+\subsection{Simulating the "reddit effect"}
+
+Due to limitations
+
+\subsection{Testing infrastructure}
+
+% TODO selenium & scala
+% anish should probably do this section
+
+\subsection{Results}
 
 \section{Future work}
+
+There remains numerous optimizations that would make \zbf more performant
+when used on a deployed, high-traffic site. We detail these potential optimization
+in this section.
 

### 2015-05-07 doc/paper/paper.tex
wrote DOM Injection Layer

@@
 \subsection{DOM injection layer}
-% Ankush
+The DOM injection layer facilitates the link between the DOM as displayed in the browser and the entire peer-to-peer system.
+The DOM injection layer creates a websocket, and then instantiates a Tracker and Signaling Channel.
+It uses these to then instantiate a Connection Manager and in turn, uses this to instantiate a Download Manager.
+
+The DOM injection layer then iterates through all the DOM elements with the \texttt{data-zf-hash} and \texttt{data-zf-fallback} attributes.
+It the values of these attributes to fetch the data via the Download Manager.
+Upon receiving the data for each web element, the DOM injection layer creates an in-memory Blob and generates URL for this object.
+It then obeys the following rules, which can easily be expanded to support other DOM elements:
+
+\begin{description}
+\item[Script elements] have the \texttt{type} of their Blob set to \texttt{text/javascript}. They then have their \texttt{src} attribute set to the URL of the in-memory Blob.
+\item[Link elements] have the \texttt{type} of their Blob set to \texttt{text/css}.
+They then have their \texttt{href} attribute set to the URL of the in-memory Blob, and \texttt{rel} attribute set to \texttt{stylesheet}.
+\item[All other elements] have the \texttt{type} of their Blob set to \texttt{application/octet-stream}.
+They then have their \texttt{src} attribute set to the URL of the in-memory Blob.
+As most browsers can intelligently determine the content of \texttt{application/octet-stream} data, this functions properly for Image nodes, and serves as the generic template for any other node.
+\end{description}
 
@@
 to change HTML such that all resources were loaded using \zbf, this would ease
-integration pains.
+integration pains and increase adoption.
 

### 2015-05-07 doc/paper/paper.tex
started reddit section

@@
 extremely slow speeds, or not loading at all, and is colloquially known as the
-"Reddit Hug of Death". \\
+"reddit hug of death" or the "reddit effect." \\
 
@@
 
-Due to limitations
+Our tests involved programmatically opening browser windows and measuring load times.
+Due to limitations of the number of browser windows that can be reasonably opened
+and the memory overhead of Chrome, our browser testing environment of choice, we could
+not reasonably open enough browser windows to exactly imitate millions of simultaneous
+visitors to a site. Instead, we simulated the "reddit effect" by throttling the content delivery
+bandwidth of the central server hosting the desired resource.
 

### 2015-05-07 eval/src/main/scala/Driver.scala
Add seedLeech function

@@ -104,13 +104,23 @@ object Driver {
     }
   }
 
+  def seedLeech(numSeeders: Int, numLeechers: Int): Float = {
+    val total = numSeeders + numLeechers
+    val (windows, drivers) = prepare(total)
+    val (seeders, leechers) = windows splitAt numSeeders
+    asyncLoadPages(seeders, true)
+    wait(seeders)
+    asyncLoadPages(leechers, false)
+    wait(leechers)
+    val times = loadTimes(leechers)
+    times.sum / times.length
+  }
+
   def main(args: Array[String]) {
-    val (windows, drivers) = prepare(12)
-    asyncLoadPages(windows, true)
-    wait(windows)
-    val times = loadTimes(windows)
-    quit(drivers)
-    println(times)
+    val s = 5
+    for (l <- 1 to 5) {
+      println(s"${s} seeders, ${l} leechers, ${seedLeech(s, l)} avg time")
+    }
   }
 
 }

### 2015-05-07 eval/src/main/scala/Driver.scala
Quit

@@ -114,11 +114,12 @@ object Driver {
     wait(leechers)
     val times = loadTimes(leechers)
     times.sum / times.length
+    quit(drivers)
   }
 
   def main(args: Array[String]) {
-    val s = 5
-    for (l <- 1 to 5) {
+    val l = 1
+    for (s <- 1 to 5) {
       println(s"${s} seeders, ${l} leechers, ${seedLeech(s, l)} avg time")
     }
   }

### 2015-05-07 eval/src/main/scala/Driver.scala
Add test

@@ -118,9 +118,14 @@ object Driver {
   }
 
   def main(args: Array[String]) {
-    val l = 1
-    for (s <- 1 to 5) {
-      println(s"${s} seeders, ${l} leechers, ${seedLeech(s, l)} avg time")
+    slt(10, 10)
+  }
+
+  def slt(maxSeed: Int, maxLeech: Int) {
+    for (s <- 1 to maxSeed) {
+      for (s <- 1 to maxLeech) {
+        println(s"${s} seeders, ${l} leechers, ${seedLeech(s, l)} avg time")
+      }
     }
   }
 

### 2015-05-07 doc/paper/paper.tex
finished reddit effect section
added placeholders to results section

@@
 The DOM injection layer facilitates the link between the DOM as displayed in the browser and the entire peer-to-peer system.
-The DOM injection layer creates a websocket, and then instantiates a Tracker and Signaling Channel.
+The DOM injection layer creates a WebSocket, and then instantiates a Tracker and Signaling Channel.
 It uses these to then instantiate a Connection Manager and in turn, uses this to instantiate a Download Manager.
@@
 
-\section{Server implementation}
+\subsection{Server implementation}
 
@@
 
-\subsection{Tracker}
+\subsubsection{Tracker}
 The tracker is hosted on a remote server and tracks client connections.
@@
 
-\subsection{WebRTC handshake channel}
+\subsubsection{WebRTC handshake channel}
 
@@
 resource, so must request it either from the central site host or from peers with the resource.
+
 Our tests launched a certain number of seeding peers, then launched a number of
@@
 \subsection{Simulating the "reddit effect"}
-
 Our tests involved programmatically opening browser windows and measuring load times.
@@
 visitors to a site. Instead, we simulated the "reddit effect" by throttling the content delivery
-bandwidth of the central server hosting the desired resource.
+bandwidth of the central server hosting the desired resource. We limited the content delivery
+rate to 64 Kb/s and performed benchmark tests that compared the performance of \zbf 
+against the HTTP content delivery latency under the throttled bandwidth conditions.
 
@@
 
-% TODO selenium & scala
+% TODO selenium with chromedriver & scala
 % anish should probably do this section
@@
 \subsection{Results}
+ % TODO
+
+\subsubsection{Scalability of \zbf}
+The first empirical analysis that we performed was determining how page load time over \zbf scales as we vary the number of users who have the page loaded (we call these users \textit{seeders}) and the number of users attempting to concurrently download the page (we call these users \textit{leechers}).
+
+\begin{figure}[h]
+% TODO: heatmap here
+\caption{Average page load time over P2P for seeders vs leechers}
+\end{figure}
+
+\subsubsection{\zbf vs HTTP}
+% TODO: figure out ratio of seeders to leechers
+Our next empirical analysis was to keep the ratio of seeders to leechers constant at X, and compare the page load times for a throttled HTTP server vs \zbf as we increase the number of users attempting to concurrently load the page.
+
+\begin{figure}[h]
+% TODO: other plot here
+% TODO: figure out ratio of seeders to leechers
+\caption{Average page load time over P2P compared to HTTP on throttled server assuming constant ratio of X seeders per leecher}
+\end{figure}
 
@@
 There remains numerous optimizations that would make \zbf more performant
-when used on a deployed, high-traffic site. We detail these potential optimization
-in this section.
+when used on a deployed, high-traffic site. We detail these potential optimizations
+in this section, along with features which could allow \zbf to handle more use cases.
 
@@
 
-% TODO cite peercdn in bibtex
+%! TODO cite peercdn in bibtex
 Currently, alternative peer-to-peer content delivery networks do exist. The three
@@
 
-% Katie
+% TODO: Katie
 \zbf is an open-sourced system

### 2015-05-07 eval/src/main/scala/Driver.scala
Implement data collection

@@ -113,20 +113,45 @@ object Driver {
     asyncLoadPages(leechers, false)
     wait(leechers)
     val times = loadTimes(leechers)
-    times.sum / times.length
     quit(drivers)
+    times.sum / times.length
+  }
+
+  def httpOnly(numClients: Int): Float = {
+    val (windows, drivers) = prepare(numClients)
+    asyncLoadPages(windows, true)
+    wait(windows)
+    val times = loadTimes(windows)
+    quit(drivers)
+    times.sum / times.length
+  }
+
+  def fixedRatio(numLeechers: Int, seedToLeechRatio: Int): Float = {
+    require (seedToLeechRatio > 0)
+    seedLeech(numLeechers * seedToLeechRatio, numLeechers)
+  }
+
+  def httpToPeers(clientRange: Seq[Int], ratio: Int) {
+    println("http vs peer to peer")
+    println(s"for p2p, ${ratio} seeds for every leech")
+    for (cl <- clientRange) {
+      println(s"${cl} clients over p2p, ${fixedRatio(cl, ratio)} ms avg load time")
+      println(s"${cl} clients over http, ${httpOnly(cl)} ms avg load time")
+    }
+  }
+
+  def seedToLeech(seedRange: Seq[Int], leechRange: Seq[Int]) {
+    println("seed x leech heat map")
+    for (s <- seedRange) {
+      for (l <- leechRange) {
+        println(s"${s} seeders, ${l} leechers, ${seedLeech(s, l)} ms avg load time")
+      }
+    }
   }
 
   def main(args: Array[String]) {
-    slt(10, 10)
-  }
-
-  def slt(maxSeed: Int, maxLeech: Int) {
-    for (s <- 1 to maxSeed) {
-      for (s <- 1 to maxLeech) {
-        println(s"${s} seeders, ${l} leechers, ${seedLeech(s, l)} avg time")
-      }
-    }
+    seedToLeech(seedRange = 1 to 10, leechRange = 1 to 10)
+    httpToPeers(clientRange = 1 to 10, ratio = 3)
   }
 
 }

### 2015-05-07 eval/src/main/scala/Driver.scala
Fix

@@ -66,18 +66,22 @@ object Driver {
   }
 
   def done(windows: Seq[Window]): Boolean = {
-    for (window <- windows) {
-      switchTo(window)
-      val jse = window._1.asInstanceOf[JavascriptExecutor]
-      var res = jse.executeScript("""
-        return (window.loadTime || "");
-        """
-        )
-      if (res == null || res.asInstanceOf[String] == "") {
-        return false
+    try {
+      for (window <- windows) {
+        switchTo(window)
+        val jse = window._1.asInstanceOf[JavascriptExecutor]
+        var res = jse.executeScript("""
+          return (window.loadTime || "");
+          """
+          )
+        if (res == null || res.asInstanceOf[String] == "") {
+          return false
+        }
       }
+      return true
+    } catch {
+      case _: WebDriverException => return false
     }
-    return true
   }
 
   def wait(windows: Seq[Window]) {

### 2015-05-08 eval/src/main/scala/Driver.scala
Add final collection parameters

@@ -155,7 +155,7 @@ object Driver {
 
   def main(args: Array[String]) {
     seedToLeech(seedRange = 1 to 10, leechRange = 1 to 10)
-    httpToPeers(clientRange = 1 to 10, ratio = 3)
+    httpToPeers(clientRange = 1 to 50, ratio = 1)
   }
 
 }

### 2015-05-08 doc/paper/paper.tex
added some new TODOs

@@
 bandwidth of the central server hosting the desired resource. We limited the content delivery
-rate to 64 Kb/s and performed benchmark tests that compared the performance of \zbf 
+rate to 512 Kb/s (64 KB/s) and performed benchmark tests that compared the performance of \zbf
 against the HTTP content delivery latency under the throttled bandwidth conditions.
@@
 
+% TODO: Analyze the plot here
+
 \subsubsection{\zbf vs HTTP}
-% TODO: figure out ratio of seeders to leechers
-Our next empirical analysis was to keep the ratio of seeders to leechers constant at X, and compare the page load times for a throttled HTTP server vs \zbf as we increase the number of users attempting to concurrently load the page.
+Our next empirical analysis was to keep the ratio of seeders to leechers constant at 1:1, and compare the page load times for a throttled HTTP server vs \zbf as we increase the number of users attempting to concurrently load the page.
 
@@
 % TODO: other plot here
-% TODO: figure out ratio of seeders to leechers
-\caption{Average page load time over P2P compared to HTTP on throttled server assuming constant ratio of X seeders per leecher}
+\caption{Average page load time over P2P compared to HTTP on throttled server assuming constant ratio of 1 seeder per leecher}
 \end{figure}
+
+% TODO: Analyze the plot here
 

### 2015-05-08 doc/paper/paper.tex
conclusions and first part of results

--- 2015-05-07 doc/paper/paper.tex
@@
 \subsubsection{Scalability of \zbf}
-The first empirical analysis that we performed was determining how page load time over \zbf scales as we vary the number of users who have the page loaded (we call these users \textit{seeders}) and the number of users attempting to concurrently download the page (we call these users \textit{leechers}).
+The first empirical analysis that we performed was determining how page load time
+over \zbf scales as we vary the number of users who have the page loaded (we call
+these users \textit{seeders}) and the number of users attempting to concurrently
+download the page (we call these users \textit{leechers}).
 
@@
 \subsubsection{\zbf vs HTTP}
+As seen in fig 1, the performance of \zbf depended on the seeder-to-leecher ratio.
+In general, the lowest latency in load time was achieved when the seeder-to-leecher
+ratio was highest. However, the system performed well in any condition with many
+seeder peers, reflecting the performance benefits provided by chunking of resources
+and parallelization of sending chunks. The system performed worst when there were many
+leechers and only a few seeders.
+
 % TODO: figure out ratio of seeders to leechers
-Our next empirical analysis was to keep the ratio of seeders to leechers constant at X, and compare the page load times for a throttled HTTP server vs \zbf as we increase the number of users attempting to concurrently load the page.
+Our next empirical analysis was to keep the ratio of seeders to leechers constant at X,
+and compare the page load times for a throttled HTTP server vs \zbf as we increase the
+number of users attempting to concurrently load the page.
 
@@
 % TODO: figure out ratio of seeders to leechers
-\caption{Average page load time over P2P compared to HTTP on throttled server assuming constant ratio of X seeders per leecher}
+\caption{Average page load time over P2P compared to HTTP on throttled server assuming
+constant ratio of X seeders per leecher}
 \end{figure}
@@
 
-% TODO: Katie
-\zbf is an open-sourced system
-that will allow developers to easily integrate a peer-to-peer CDN to expedite
-content delivery to clients even when operating under heavy load.
+\zbf is an open-sourced system that will allow developers to easily utilize
+a peer-to-peer CDN to increase the content delivery bandwidth of their sites,
+even when operating under heavy request loads. Preliminary data shows that
+the system performs well under medium and high workloads, and when the
+seeder-to-leecher ratio is high. Future work could refine the system
+such that it works well in a wide variety of scenarios. Our results show that peer-to-peer
+CDNs are a promising low-cost alternative to CDNs that require on an extensive
+network of server and server infrastructure.
 

### 2015-05-08 doc/paper/paper.tex
finish results description

@@
 
-\begin{figure}[h]
+\begin{figure}[heatmap.pdf]
 % TODO: heatmap here
@@
 
-\subsubsection{\zbf vs HTTP}
-As seen in fig 1, the performance of \zbf depended on the seeder-to-leecher ratio.
+As seen in figure 1, the performance of \zbf depended on the seeder-to-leecher ratio.
 In general, the lowest latency in load time was achieved when the seeder-to-leecher
@@
 
+\subsubsection{\zbf vs HTTP}
 % TODO: figure out ratio of seeders to leechers
@@
 
-\begin{figure}[h]
+\begin{figure}[lineplot.pdf]
 % TODO: other plot here
@@
 \end{figure}
+
+As seen in figure 2, \zbf performed well in comparison to loading content over HTTP.
+While both experienced increases in content delivery latency with increasing numbers
+of peers requesting content, in general \zbf had lower latency than HTTP. Note
+that our simulated "reddit effect" implies hundreds of thousands of other
+simultaneous connection; however, since we are simulating the effect, these
+imaginary peers cannot distribute content to new peers. So, \zbf could potentially
+provide an even greater latency drop with more active seeding peers, which would
+be the case in a real-world scenario.
 

### 2015-05-08 doc/paper/paper.tex
Add figures

@@
 \newcommand{\projtitle}{\zbf: A Transparent Peer-to-Peer CDN}
-\newcommand{\inclfigure}[3]{
+\newcommand{\inclfigure}[4]{
     \begin{figure}
         \begin{centering}
-            \includegraphics[width=.8\linewidth]{#2}
-            \caption{#3}
+            \includegraphics[angle=#3,width=.8\linewidth]{#2}
+            \caption{#4}
             \label{#1}
@@
 extremely slow speeds, or not loading at all, and is colloquially known as the
-"reddit hug of death" or the "reddit effect." \\
+``reddit hug of death'' or the ``reddit effect.'' \\
 
@@
 The \zbf architecture consists of several loosely-connected components (see
-figure~\ref{fig:components}). At the highest level, there is a download manager that
+\Cref{fig:components}). At the highest level, there is a download manager that
 provides a reliable download service. It relies on the tracker interface and
@@
 
-\inclfigure{fig:components}{components.pdf}{
+\inclfigure{fig:components}{components.pdf}{0}{
     Relationship between different client-side components of the \zbf
@@
 
-\subsection{Simulating the "reddit effect"}
+\subsection{Simulating the ``reddit effect''}
 Our tests involved programmatically opening browser windows and measuring load times.
@@
 not reasonably open enough browser windows to exactly imitate millions of simultaneous
-visitors to a site. Instead, we simulated the "reddit effect" by throttling the content delivery
+visitors to a site. Instead, we simulated the ``reddit effect'' by throttling the content delivery
 bandwidth of the central server hosting the desired resource. We limited the content delivery
@@
 \subsection{Results}
- % TODO
 
@@
 
-\begin{figure}[heatmap.pdf]
-% TODO: heatmap here
-\caption{Average page load time over P2P for seeders vs leechers}
-\end{figure}
+\inclfigure{fig:heatmap}{heatmap.eps}{-90}{
+    Average page load time over P2P for seeders vs leechers.
+}
 
-As seen in figure 1, the performance of \zbf depended on the seeder-to-leecher ratio.
-In general, the lowest latency in load time was achieved when the seeder-to-leecher
-ratio was highest. However, the system performed well in any condition with many
-seeder peers, reflecting the performance benefits provided by chunking of resources
-and parallelization of sending chunks. The system performed worst when there were many
-leechers and only a few seeders.
+As seen in \Cref{fig:heatmap}, the performance of \zbf depended on the
+seeder-to-leecher ratio. In general, the lowest latency in load time was
+achieved when the seeder-to-leecher ratio was highest. However, the system
+performed well in any condition with many seeder peers, reflecting the
+performance benefits provided by chunking of resources and parallelization of
+sending chunks. The system performed worst when there were many leechers and
+only a few seeders.
 
 \subsubsection{\zbf vs HTTP}
-% TODO: figure out ratio of seeders to leechers
-Our next empirical analysis was to keep the ratio of seeders to leechers constant at X,
-and compare the page load times for a throttled HTTP server vs \zbf as we increase the
-number of users attempting to concurrently load the page.
 
-\begin{figure}[lineplot.pdf]
-% TODO: other plot here
-% TODO: figure out ratio of seeders to leechers
-\caption{Average page load time over P2P compared to HTTP on throttled server assuming
-constant ratio of X seeders per leecher}
-\end{figure}
+Our next empirical analysis was to keep the ratio of seeders to leechers
+constant at 1, and compare the page load times for a throttled HTTP server vs
+\zbf as we increase the number of users attempting to concurrently load the
+page.
 
-As seen in figure 2, \zbf performed well in comparison to loading content over HTTP.
-While both experienced increases in content delivery latency with increasing numbers
-of peers requesting content, in general \zbf had lower latency than HTTP. Note
-that our simulated "reddit effect" implies hundreds of thousands of other
-simultaneous connection; however, since we are simulating the effect, these
-imaginary peers cannot distribute content to new peers. So, \zbf could potentially
-provide an even greater latency drop with more active seeding peers, which would
-be the case in a real-world scenario.
+\inclfigure{fig:scalability}{scalability.eps}{-90}{
+    Average page load time over P2P compared to HTTP on throttled server
+    assuming constant ratio of 1 seeder per leecher.
+}
+
+As seen in \Cref{fig:scalability}, \zbf performed well in comparison to
+loading content over HTTP. While both experienced increases in content delivery
+latency with increasing numbers of peers requesting content, in general \zbf
+had lower latency than HTTP. Note that our simulated ``reddit effect'' implies
+hundreds of thousands of other simultaneous connection; however, since we are
+simulating the effect, these imaginary peers cannot distribute content to new
+peers. So, \zbf could potentially provide an even greater latency drop with
+more active seeding peers, which would be the case in a real-world scenario.
 

### 2015-05-08 doc/paper/paper.tex
Fix

@@
 It is common for personal blogs and other small websites to gain sudden attention
-on large, high-traffic websites such as Reddit. Since these websites usually
+on large, high-traffic websites such as reddit. Since these websites usually
 experience much smaller traffic loads, the hardware devoted to hosting them

### 2015-05-08 doc/paper/paper.tex
Fix heat plot

@@
 bandwidth of the central server hosting the desired resource. We limited the content delivery
-rate to 64 Kb/s and performed benchmark tests that compared the performance of \zbf
+rate to 64 KB/s and performed benchmark tests that compared the performance of \zbf
 against the HTTP content delivery latency under the throttled bandwidth conditions.

### 2015-05-08 doc/paper/paper.tex
added missing citations
Add testing infrastructure section

@@
 
-% TODO selenium with chromedriver & scala
-% anish should probably do this section
+Our testing infrastructure was made up of a virtual machine hosting our
+website, a tracker running on the host machine, and a collection of web
+browsers acting as clients. All test code ran on the same physical machine. We
+used Vagrant to provision an Ubuntu 14.04 LTS virtual machine running nginx
+1.4.6 to serve a test page designed for benchmarking. To simulate a
+low-resource server / heavy loads, we used kernel traffic shaping to limit the
+outbound bandwidth of the virtual machine. To simulate browser clients, we
+wrote a test driver in Scala that made use of Selenium WebDriver and
+ChromeDriver to launch and control Google Chrome browser windows. The test
+driver spawned and communicated with browser windows and benchmark code through
+Javascript so it could measure page load times.
 
@@
 It is possible to add functionality such that \zbf can construct
-\texttt{ReadableStream}s (as specified by the Streams standard)
-%TODO: cite https://streams.spec.whatwg.org
+\texttt{ReadableStream}s (as specified by the Streams standard~\cite{whatwg:streams})
 from the chunks of data as it receives them. Using this stream, the DOM injection
@@
 
-%! TODO cite peercdn in bibtex
 Currently, alternative peer-to-peer content delivery networks do exist. The three

### 2015-05-08 doc/paper/paper.tex
Rephrase start of abstract

@@
 \begin{abstract}
-\zbf is a peer-to-peer system based on the BitTorrent protocol that uses WebRTC
-to distribute content between peers. \zbf provides an easily accessible way for
-developers to alleviate content delivery bandwidth concerns by marking DOM elements
-such that \zbf will fetch these resources from peers with that resource. The \zbf
-system has server-side tracker and WebRTC signaling channel components, as well
-as client-side scripting that requests and delivers content between peers.
-This version of the system implements basic chunking, parallelism, and fault tolerance.
-In this paper, we describe the motivation for \zbf and the design and implementation of the
-different components that comprise the system. We then detail future improvements
-that could be made to increase the robustness and performance of the overall system.
+
+\zbf is a peer-to-peer content delivery network. The system uses WebRTC to
+cache and distribute content between peers. \zbf provides an easily accessible
+way for developers to alleviate content delivery bandwidth concerns by marking
+DOM elements such that \zbf will fetch these resources from peers with that
+resource. The \zbf system has server-side tracker and WebRTC signaling channel
+components, as well as client-side scripting that requests and delivers content
+between peers. This version of the system implements basic chunking,
+parallelism, and fault tolerance. In this paper, we describe the motivation for
+\zbf and the design and implementation of the different components that
+comprise the system. We then detail future improvements that could be made to
+increase the robustness and performance of the overall system.
+
 \end{abstract}

### 2015-05-08 doc/paper/paper.tex
Reword

@@
 
-Typical means for dealing with this situation involve utilizing Content Delivery
-Networks (CDNs), but these are usually out of the budgetary constraints for
-websites which only experience such loads on an occasional basis. An ideal
-solution would be a lightweight means to mimic the benefits of an ordinary
-CDN, which is typically backed by a robust network of machines. \\
+Typical means for dealing with this situation involve utilizing Content
+Delivery Networks (CDNs), but these are expensive, especially for websites
+which only experience such high loads on an occasional basis. An ideal solution
+would be a lightweight means to mimic the benefits of an ordinary CDN, which is
+typically backed by a robust network of machines. \\
 

### 2015-05-08 doc/paper/paper.tex
Fix

@@
 extremely slow speeds, or not loading at all, and is colloquially known as the
-``reddit hug of death'' or the ``reddit effect.'' \\
+``reddit hug of death'' or the ``reddit effect.''
 
@@
 would be a lightweight means to mimic the benefits of an ordinary CDN, which is
-typically backed by a robust network of machines. \\
+typically backed by a robust network of machines.
 
@@
 lightweight client-side component requests resources from peers and distributes
-resources in response to peer requests. \\
+resources in response to peer requests.
 
@@
 with BitTorrent trackers, any developer could host their own tracker and service
-it to connect peers requesting a resource with peers distributing the resource. \\
+it to connect peers requesting a resource with peers distributing the resource.
 
@@
 code only runs when a user is currently visiting the website, therefore adding
-no burden to the user from constant background processes. \\
+no burden to the user from constant background processes.
 
@@
 For an existing website to utilize \zbf, the developer simply needs
-to make two changes to the DOM elements. \\
+to make two changes to the DOM elements.
 
@@
 and (2) provide a URL to be used in the event that the peer-to-peer network
-is unable to serve the content. \\
+is unable to serve the content.
 
@@
 the central tracker for information about peers and file sizes, and the
-connection manager provides an interface for peer-to-peer message transfer. \\
+connection manager provides an interface for peer-to-peer message transfer.
 
@@
 The download manager then evenly distributes requests for these chunks
-among the peers with the resource. \\
+among the peers with the resource.
+
 Requests for chunks time out on a per-chunk basis. We track the time \zbf
@@
 chunk had been corrupted or compromised, all chunks for the file would need to be
-downloaded, combined, and verified again. \\
+downloaded, combined, and verified again.
 

### 2015-05-08 doc/paper/paper.tex
Update

@@
 
-The \zbf client-side code runs purely in the browser, and is completely transparent
-to the user. The user does not have to install any application on their
-computer to obtain desired resources peer-to-peer. As a result, the \zbf client
-code only runs when a user is currently visiting the website, therefore adding
-no burden to the user from constant background processes.
+The \zbf client-side code runs purely in the browser and is completely
+transparent to the user. The user does not have to install any application on
+their computer to obtain desired resources peer-to-peer. As a result, the \zbf
+client code only runs when a user is currently visiting the website, adding no
+burden to the user from constant background processes.
 
 In designing \zbf, we took into consideration the unique problems presented
-by browser-to-browser content streaming. Website visitor churn is often very
+by browser-to-browser content sharing. Website visitor churn is often very
 high with any type of website; our system had to be robust under these common
@@
 \zbf divides assets into chunks; chunks are individually requested and
-sent between peers. We use a standard chunk size of 10240 bytes in our
+sent between peers. We use a standard chunk size of 25 KB in our
 implementation; preliminary tests showed this chunk size to be reasonable.

### 2015-05-08 doc/paper/paper.tex
Fix

@@
 
-We tested \zbf on a simple site that loads one large 768KB image from a remote server.
+We tested \zbf on a simple site that loads one large 768 KB image from a remote server.
 In our tests, we compare page load times using both plain HTTP and \zbf in a range of
@@
 \inclfigure{fig:heatmap}{heatmap.eps}{-90}{
-    Average page load time over P2P for seeders vs leechers.
+    Average page load time (lower is better) over P2P for seeders vs leechers.
 }
@@
 \inclfigure{fig:scalability}{scalability.eps}{-90}{
-    Average page load time over P2P compared to HTTP on throttled server
-    assuming constant ratio of 1 seeder per leecher.
+    Average page load time (lower is better) over P2P compared to HTTP on
+    throttled server assuming constant ratio of 1 seeder per leecher.
 }

### 2015-05-08 doc/paper/paper.tex
Fix

@@
 
-\zbf is an open-sourced system that will allow developers to easily utilize
-a peer-to-peer CDN to increase the content delivery bandwidth of their sites,
-even when operating under heavy request loads. Preliminary data shows that
-the system performs well under medium and high workloads, and when the
-seeder-to-leecher ratio is high. Future work could refine the system
-such that it works well in a wide variety of scenarios. Our results show that peer-to-peer
-CDNs are a promising low-cost alternative to CDNs that require on an extensive
-network of server and server infrastructure.
+\zbf is an open-sourced system that will allow developers to easily utilize a
+peer-to-peer CDN to increase the content delivery bandwidth of their sites,
+even when operating under heavy request loads. Preliminary data shows that the
+system performs well under medium and high workloads, and when the
+seeder-to-leecher ratio is high. Future work could refine the system such that
+it works well in a wide variety of scenarios. Our results show that
+peer-to-peer CDNs are a promising low-cost alternative to CDNs that require an
+extensive network of server and server infrastructure.
 
